---
title: "Colombia plots and tables for the Hope Groups paper - partial credit model v251224"
date: "2025-12-30"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

We found the PCM model (v251224) performed best on the Colombia data among the three IRT models considered (ordered logistic model, credit model, partial credit model). This vignette generates plots and tables for the Hope Groups paper using the partial credit model v251224.

# Standalone model fit

## Load/Install packages

```{r load-packages, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Install and load packages
packages <- c(
    "cowplot",
    "data.table",
    "here",
    "purrr",
    "formatR",
    "ggplot2",
    "ggsci",
    "ggpubr",
    "hexbin",
    "bayesplot",
    "knitr",
    "kableExtra",
    "cmdstanr",
    "loo",
    "polycor",
    "GGally"
)
invisible(lapply(packages, library, character.only = TRUE))
```

```{r source-functions, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
source(here::here("R", "read_data_colombia.R"))
source(here::here("R", "train_test_split_data.R"))
source(here::here("R", "fit_credit_model.R"))
source(here::here("R", "fit_ordered_logit_model.R"))
source(here::here("R", "fit_partial_credit_model.R"))
```

## Data loading and pre-processing

```{r define-data-locations, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define directories
if (grepl("^/rds/general/user/or105", here::here())) {
    # Working on HPC
    on_hpc <- TRUE
    dir_data <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups/data"
    dir_out_base <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups"
} else {
    # Working locally
    on_hpc <- FALSE
    dir_data <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/data"
    dir_out_base <- "/Users/or105/sandbox"
}

# Define file names
file_data <- file.path(dir_data, "Colombia_data_baseline_endline_itemised_250927.csv")
file_data_quasi <- file.path(dir_data, "Colombia_data_quasi_assignments_250927.csv")
file_data_Ukraine <- file.path(dir_data, "Ukraine_Hope_Groups_Baseline_Endline_Wide_Aug6.csv")


set.seed(42L)
seed <- c(123L)
```

```{r load-and-preprocess-data, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}

# Read in data from Ukraine
dp <- as.data.table(read.csv(file_data_Ukraine))
tmp <- subset(dp, select = c('UniqueID', colnames(dp)[grepl('.x$',colnames(dp))] ))
tmp2 <- subset(dp, select = c('UniqueID', colnames(dp)[grepl('.y$',colnames(dp))] ))
setnames(tmp, old = colnames(tmp)[grepl('.x$',colnames(tmp))],
         new = gsub('.x$','',colnames(tmp)[grepl('.x$',colnames(tmp))]))
setnames(tmp2, old = colnames(tmp2)[grepl('.y$',colnames(tmp2))],
         new = gsub('.y$','',colnames(tmp2)[grepl('.y$',colnames(tmp2))]))
tmp <- subset(tmp, select = !grepl('^Scale_',colnames(tmp)) )
stopifnot(setdiff(colnames(tmp), colnames(tmp2)) == character(0))
stopifnot(setdiff(colnames(tmp2), colnames(tmp)) == character(0))
dp <- rbind(tmp, tmp2) 
setnames(
    dp,
    c("UniqueID", "Timepoint", "f_name"),
    c("pid", "time_label", "f_label")
)

# Separate out meta data/ covariates
col_meta <- c("marital_status", "living_partner", "served_partnered", 
    "demo_sex_labelled", "age_range_labelled", "edu_level_grped.labelled", "income_labelled", "country",        
    "displacement_status", "shelter_now", "children", "health_disability2", "under_12months",        
    "btwn_1_3_yrs", "btwn_4_7_yrs", "btwn_8_12yrs", "assistance.mhpss",  
    "partner_sharing", "partner_conflict", "unhappy_internal", "facilitator_relationship", 
    "spillover_frequency", "spillover_book", "past_programs", "spiritual_strength", "resources_afterHG", "life_worse_me", "life_worse_family", "shelter_now_clean", "training", "training_type")       
dmeta <- subset(dp, select = c("pid", "time_label", col_meta))

# Remove non primary outcome data
set(dp, NULL, col_meta, NULL)
set(dp, NULL, c('PHQ4_total_weight',"Physical_Emotional_Violence7",
"Positive_Parenting7", "Parental_Involvement7", "Parental_Monitoring7", 
"Resilience7", "Child_Wellbeing7", "IPV_Prevention7", "Key"), NULL)

# Clean up outcome labels
setnames(
    dp,
    c("Physical_Emotional_Violence", "physic_punish", "ICAST_EA_scream"),   #TODO "physic_punish"
    c("CG-VIO_agg", "CG-VIO_ph-punish", "CG-VIO_scream")
)

setnames(
    dp,
    c(
        "CAREGIVER_MENTAL_HEALTH", "nervous", "hopeless", "restless",   # TODO all of these
        "sad", "effort", "worthless"
    ),
    c(
        "CG-MH_agg", "CG-MH_nervous", "CG-MH_hopeless", "CG-MH_restless",
        "CG-MH_sad", "CG-MH_effort", "CG-MH_worthless"
    )
)

setnames(
    dp,
    c("POSITIVE_PARENTING", "praise", "play"),                      # TODO all of these
    c("CG-POS_agg", "CG-POS_praise", "CG-POS_play")
)
    
setnames(                                                               # TODO safe_time, child_safe
    dp,
    c("Parental_Monitoring", "safe_time", "child_safe"),
    c("CG-MONITOR-CHI_agg", "CG-MONITOR-CHI_safe-time","CG-MONITOR-CHI_child-safe")
)

setnames(                                                               # TODO help_learn, child_problems                     
    dp,
    c("Parental_Involvement", "help_learn", "child_problems"),
    c("CG-INVOLVE_agg", "CG-INVOLVE_help-learn", "CG-INVOLVE_child-problems")
)

setnames(                                                               # TODO all of these
    dp,
    c("CHILD_BEHAVIOURAL_ISSUES", "angry", "unhappy", "no_interest"),
    c("CHI-BEHAVIOUR_agg", "CHI-BEHAVIOUR_angry", "CHI-BEHAVIOUR_unhappy","CHI-BEHAVIOUR_no-interest")
)

setnames(
        dp,
        c("CESD_depressed", "selfcare", "Resilience", "NONVIOLENT_DISCIPLINE"), #TODO NONVIOLENT_DISCIPLINE
        c("CG-DEPRESSION", "CG-SELFCARE", "CG-RESILIENCE", "CG-NONVIOLENT-DISCIPLINE")
    )


# END TODO
    
    
    
    
    
    # Clean up date
    set(
        dp, NULL, "submission_date",
        dp[, as.Date(submission_date, format = "%m/%d/%y")]
    )

    # Set time id
    dp[, time := as.integer(time_label == "Endline")]

    # Remove participant with double endline - remove last record
    dp <- subset(
        dp,
        !(pid %in% c("otmar20231963") & submission_date == "2024-12-12")
    )

    # Remove participants with only baseline records
    # as we are interested in pre-post comparison
    tmp <- dp[, list(n = length(submission_date)), by = "pid"]
    tmp <- subset(tmp, n == 2, select = pid)
    dp <- merge(tmp, dp, by = "pid")

    # Set participant id
    tmp <- data.table(pid = dp[, sort(unique(pid))])
    tmp[, pid_new := seq_len(nrow(tmp))]
    dp <- merge(dp, tmp, by = "pid")
    setnames(dp, c("pid", "pid_new"), c("pid_label", "pid"))

    # Set facilitator id
    tmp <- data.table(f_label = dp[, sort(unique(f_label))])
    tmp[, fid := seq_len(nrow(tmp))]
    dp <- merge(dp, tmp, by = "f_label")

    # Bring table into long format
    dp <- data.table::melt(
        dp,
        id.vars = c(
            "time", "time_label", "pid", "pid_label", "fid",
            "f_label", "submission_date", "d_year"
        ),
        variable.name = "item_label",
        value.name = "y"
    )

    # Remove NA's
    dp <- subset(dp, !is.na(y))

    # Define character values for y
    dp[, y_label := NA_character_]
    tmp <- dp[, which(grepl("^CG-MH_.*", item_label) & !grepl("agg", item_label))]
    set(
        dp,
        tmp,
        "y_label",
        c(
            "a - none of the time", "b - a little of the time",
            "c - some of the time", "d - most of the time",
            "e - all of the time"
        )[dp[tmp, y] + 1L]
    )
    tmp <- dp[, which(is.na(y_label) & !grepl("agg", item_label))]
    set(dp, tmp, "y_label", dp[tmp, paste0(as.character(y), " of 7 days")])

    # Show value mins and maxs
    dp[, list(ymin = min(y), ymax = max(y)), by = "item_label"]

    dit <- unique(subset(dp, select = "item_label"))
    dit[, item_type := ifelse(
        grepl("CG-MH", item_label), "categorical", "out-of-7"
    )]
    dit[, item_high_label := ifelse(
        grepl("CG-MH|CG-DEPRESSION|CG-VIO|CHI-BEHAVIOUR", item_label),
        "lower_is_better",
        "higher_is_better"
    )]
    dit[, group_label := factor(gsub("([^_]+)_([^_]+)", "\\1", item_label))]
    dit[, item_label_short := gsub("([^_]+)_([^_]+)", "\\2", item_label)]
    set(dit, dit[, which(grepl("^CG", item_label_short))], "item_label_short", "")
    dit[, group_label_long := group_label]
    tmp <- dit[, levels(group_label_long)]
    tmp <- sapply(tmp, function(x) {
        switch(x,
            "CG-MH" = "Caregiver mental health",
            "CG-VIO" = "Caregiver exercising physical or emotional violence",
            "CG-MONITOR-CHI_agg" = "Child monitoring",
            "CG-INVOLVE" = "Caregiver involvement",
            "CHI-BEHAVIOUR" = "Child behavioural issues",
            "CG-DEPRESSION" = "Caregiver depression",
            "CG-SELFCARE" = "Caregiver self-care",
            "CG-RESILIENCE" = "Caregiver resilience",
            "CG-POS" = "Caregiver positive parenting",
            "CG-MONITOR-CHI" = "Caregiver monitoring child",
            "CG-NONVIOLENT-DISCIPLINE" = "Caregiver exercising nonviolent discipline",
            x
        )
    })
    levels(dit$group_label_long) <- tmp
    dit[, endpoint_measure := sapply(item_type, function(x) {
        switch(x,
            "categorical" = "events occurring most or all of the time",
            "out-of-7" = "mean days in week",
            x
        )
    })]

    list(dp = dp, dit = dit, dmeta = dmeta)



# Read in data from Colombia
tmp <- read_data_colombia(file_data)
dp <- copy(tmp$dp)
dit <- copy(tmp$dit)
dmeta <- copy(tmp$dmeta)

# Preprocess data
dp1 <- subset(dp, !grepl("agg", item_label))
dp1[, time := time + 1L]
dp1[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1$item_label)),
    time = unique(dp1$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1 <- merge(dp1, tmp, by = c("item_label", "time"))
setkey(dp1, pid, time, item_label)
dp1[, oid := .I]
setkey(dp1, oid)
tmp <- dp1[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1 <- merge(dp1, tmp, by = c("item_type", "oid"))
setkey(dp1, pid, time, item_label)
```

## Run partial credit model v251224 on Colombia data

```{r setup-pcm-directories-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-251224")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix_pcm <- file.path(dir_out_pcm, "pcm_1")
output_file_prefix <- file.path(dir_out_pcm, "pcm_1")
```

```{r compile-stan-model-pcm-v251224, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "partial_credit_model_2cats_v251224.stan")
pcm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r pcm-fit-on-training-data-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
rds_file <- paste0(output_file_prefix, "_fit_alldata_stan.rds")
if (!file.exists(rds_file)) {
    cat("\n=== Running partial credit model v251224===\n")
    pcm_fit <-fit_partial_credit_model(
            dit,
            dp1,
            output_file_prefix = paste0(output_file_prefix, "_fit_alldata"),
            stan_file = here::here("src", "stan", "partial_credit_model_2cats_v251224.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 1000L,
            seed = seed,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
}
gc()
```

# Plots and Tables

## Create primary endpoints for each group of items

Aggregate most + all of the time and compute mean for out-of-7

```{r colombia-endpoints, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, cache=TRUE}

# Aggregate categorical probabilities for most + all of the time
po <- pcm_fit$draws(
    variables = c("cat1_ordered_prob_by_obs"),
    inc_warmup = FALSE,
    format = "draws_df"
)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po[, y_stan := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\3", variable))]
po[, oidt := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\2", variable))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1[item_type == "categorical", ],
    select = c(oidt, pid, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("oidt"))
po <- subset(po, y_stan > 3)
po <- po[,
    list(y_stan = 45, prob = sum(prob)),
    by = c(".draw", "oidt", "pid", "item_label", "item_time_id", "item_type", "time_label")
]
po <- merge(po, subset(dit, select = c(item_type, item_label, group_label)), by = c("item_type", "item_label"))
po <- po[,
    list(prob = mean(prob)),
    by = c(".draw", "pid", "item_type", "time_label", "group_label")
]
po <- data.table::dcast(po,
    .draw + pid + item_type + group_label ~ time_label,
    value.var = "prob"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po[, diff := Baseline - Endline]
po[, ratio := 1 - Endline / Baseline]
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- po[,
    list(diff = mean(diff), ratio = mean(ratio), diff2 = mean(diff2), ratio2 = mean(ratio2), bl = mean(Baseline), el = mean(Endline)),
    by = c(".draw", "item_type", "group_label")
]
po <- melt(po,
    id.vars = c(".draw", "item_type", "group_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "bl", "el")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "group_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + group_label + variable ~ summary_name,
    value.var = "summary_value"
)
tmp <- unique(subset(dit, select = c(item_type, group_label, group_label_long, item_high_label)))
pos <- merge(pos, tmp, by = c("item_type", "group_label"))
pos_cat1 <- copy(pos)
po <- NULL
gc()

# Compute mean for out-of-7 responses
po <- pcm_fit$draws(
    variables = c("cat2_ordered_prob_by_obs"),
    inc_warmup = FALSE,
    format = "draws_df"
)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po[, y_stan := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\3", variable))]
po[, oidt := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\2", variable))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1[item_type == "out-of-7", ],
    select = c(oidt, pid, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("oidt"))
po <- po[,
    list(mean = sum((y_stan - 1) * prob)),
    by = c(".draw", "oidt", "pid", "item_label", "item_time_id", "item_type", "time_label")
]
po <- merge(po, subset(dit, select = c(item_type, item_label, group_label)), by = c("item_type", "item_label"))
po <- po[,
    list(mean = mean(mean)),
    by = c(".draw", "pid", "item_type", "time_label", "group_label")
]
po <- data.table::dcast(po,
    .draw + pid + item_type + group_label ~ time_label,
    value.var = "mean"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po <- merge(po,
    unique(subset(dit, select = c(item_type, group_label, item_high_label))),
    by = c("item_type", "group_label")
)
po[, diff := NA_real_]
po[, ratio := NA_real_]
tmp <- po[, which(item_high_label == "lower_is_better")]
set(po, tmp, "diff", po[tmp, Baseline - Endline])
set(po, tmp, "ratio", po[tmp, 1 - Endline / Baseline])
tmp <- po[, which(item_high_label == "higher_is_better")]
set(po, tmp, "diff", po[tmp, Endline - Baseline])
set(po, tmp, "ratio", po[tmp, Endline / Baseline - 1])
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- po[,
    list(diff = mean(diff), ratio = mean(ratio), diff2 = mean(diff2), ratio2 = mean(ratio2), bl = mean(Baseline), el = mean(Endline)),
    by = c(".draw", "item_type", "group_label", "item_high_label")
]
po <- melt(po,
    id.vars = c(".draw", "item_type", "group_label", "item_high_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "bl", "el")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "group_label", "item_high_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + group_label + item_high_label + variable ~ summary_name,
    value.var = "summary_value"
)
tmp <- unique(subset(dit, select = c(item_type, group_label, group_label_long, item_high_label)))
pos <- merge(pos, tmp, by = c("item_type", "group_label", "item_high_label"))
pos_cat2 <- copy(pos)
po <- NULL
gc()

pos <- rbind(pos_cat1, pos_cat2, fill = TRUE)

cat("\nwrite endpoints to file=", paste0(output_file_prefix, "_primary_endpoints_grouped.rds"), "\n")
saveRDS(pos,
    file = paste0(output_file_prefix, "_primary_endpoints_grouped.rds"))
```

## Create primary endpoints for each item

Aggregate most + all of the time and compute mean for out-of-7

```{r colombia-endpoints, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, cache=TRUE}

# Aggregate categorical probabilities for most + all of the time
po <- pcm_fit$draws(
    variables = c("cat1_ordered_prob_by_obs"),
    inc_warmup = FALSE,
    format = "draws_df"
)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po[, y_stan := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\3", variable))]
po[, oidt := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\2", variable))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1[item_type == "categorical", ],
    select = c(oidt, pid, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("oidt"))
po <- subset(po, y_stan > 3)
po <- po[,
    list(y_stan = 45, prob = sum(prob)),
    by = c(".draw", "oidt", "pid", "item_label", "item_time_id", "item_type", "time_label")
]
po <- data.table::dcast(po,
    .draw + pid + item_type + item_label ~ time_label,
    value.var = "prob"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po[, diff := Baseline - Endline]
po[, ratio := 1 - Endline / Baseline]
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- po[,
    list(diff = mean(diff), ratio = mean(ratio), diff2 = mean(diff2), ratio2 = mean(ratio2), bl = mean(Baseline), el = mean(Endline)),
    by = c(".draw", "item_type", "item_label")
]
po <- melt(po,
    id.vars = c(".draw", "item_type", "item_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "bl", "el")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "item_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + item_label + variable ~ summary_name,
    value.var = "summary_value"
)
pos <- merge(pos, dit, by = c("item_type", "item_label"))
pos_cat1 <- copy(pos)
po <- NULL
gc()

# Compute mean for out-of-7 responses
po <- pcm_fit$draws(
    variables = c("cat2_ordered_prob_by_obs"),
    inc_warmup = FALSE,
    format = "draws_df"
)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po[, y_stan := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\3", variable))]
po[, oidt := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\2", variable))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1[item_type == "out-of-7", ],
    select = c(oidt, pid, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("oidt"))
po <- po[,
    list(mean = sum((y_stan - 1) * prob)),
    by = c(".draw", "oidt", "pid", "item_label", "item_time_id", "item_type", "time_label")
]
po <- data.table::dcast(po,
    .draw + pid + item_type + item_label ~ time_label,
    value.var = "mean"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po <- merge(po,
    subset(dit, select = c(item_type, item_label, item_high_label)),
    by = c("item_type", "item_label")
)
po[, diff := NA_real_]
po[, ratio := NA_real_]
tmp <- po[, which(item_high_label == "lower_is_better")]
set(po, tmp, "diff", po[tmp, Baseline - Endline])
set(po, tmp, "ratio", po[tmp, 1 - Endline / Baseline])
tmp <- po[, which(item_high_label == "higher_is_better")]
set(po, tmp, "diff", po[tmp, Endline - Baseline])
set(po, tmp, "ratio", po[tmp, Endline / Baseline - 1])
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- po[,
    list(diff = mean(diff), ratio = mean(ratio), diff2 = mean(diff2), ratio2 = mean(ratio2), bl = mean(Baseline), el = mean(Endline)),
    by = c(".draw", "item_type", "item_label", "item_high_label")
]
po <- melt(po,
    id.vars = c(".draw", "item_type", "item_label", "item_high_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "bl", "el")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "item_label", "item_high_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + item_label + item_high_label + variable ~ summary_name,
    value.var = "summary_value"
)
pos <- merge(pos, dit, by = c("item_type", "item_label", "item_high_label"))
pos_cat2 <- copy(pos)
po <- NULL
gc()

pos <- rbind(pos_cat1, pos_cat2, fill = TRUE)

cat("\nwrite endpoints to file=", paste0(output_file_prefix, "_primary_endpoints_detailed.rds"), "\n")
saveRDS(pos,
    file = paste0(output_file_prefix, "_primary_endpoints_detailed.rds"))
```

## Supplementary Table 1

```{r make-supp-table-1, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
pos <- readRDS(paste0(output_file_prefix, "_primary_endpoints_grouped.rds"))
pos <- subset(pos, variable %in% c('bl','el','ratio2','diff2'))

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope \\\\and Resilience"]
pos[group_label_long == "Caregiver exercising nonviolent discipline", group_label_long := "Caregiver exercising \\\\ nonviolent discipline"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression \\\\ and Anxiety']

# Recode item_high_label for display
pos[, item_high_label := ifelse(item_high_label == "lower_is_better", "Lower", "Higher")]
pos[, item_high_label := factor(item_high_label, levels = c("Lower", "Higher"))]

# Format numbers
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp] * 100, 1))
}
tmp <- pos[, which(!(variable %in% c('ratio2') | item_type == 'categorical'))]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp], 1))
}
pos[, value_string := NA_character_]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    " \\\\ (",
    sprintf("%.1f", q_lower),
    ", ",
    sprintf("%.1f", q_upper),
    ")}"
)])
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    "\\% \\\\ (",
    sprintf("%.1f", q_lower),
    "\\%, ",
    sprintf("%.1f", q_upper),
    "\\%)}"
)])

# Recode item_type for display
pos[item_type == "categorical", item_type := "$^\\dagger$"]
pos[item_type == "out-of-7", item_type := "$^\\ddagger$"]

# Reshape for table
pos <- dcast.data.table(pos,
    item_type + group_label_long + item_high_label ~ variable,
    value.var = "value_string"
)

# Create outcome domain with superscript for footnote
pos[, outcome_domain := paste0('\\makecell{',group_label_long, item_type, "}")]
pos[, type := ""]

# Save as CSV (include original columns for reference)
fwrite(pos, file = paste0(output_file_prefix, "_supp_table_1.csv"))


pos1 <- subset(pos, !group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

pos2 <- subset(pos, group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

# Reorder and select columns for display 
pos1 <- pos1[, c("type","outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2")]
pos2 <- pos2[, c("type","outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2")]

# Recode names for display
setnames(pos1,
    old = c("type", "outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

setnames(pos2,
    old = c("type", "outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

# Create LaTeX table
latex_table1 <- kable(pos1, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table1 <- strsplit(latex_table1, "\n")[[1]]
latex_table2 <- kable(pos2, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table2 <- strsplit(latex_table2, "\n")[[1]]

# Create standalone LaTeX document with threeparttable for footnotes
latex_doc <- paste0(
    "\\documentclass{article}\n",
    "\\usepackage{booktabs}\n",
    "\\usepackage{longtable}\n",
    "\\usepackage{array}\n",
    "\\usepackage{multirow}\n",
    "\\usepackage{wrapfig}\n",
    "\\usepackage{float}\n",
    "\\usepackage{colortbl}\n",
    "\\usepackage{pdflscape}\n",
    "\\usepackage{tabu}\n",
    "\\usepackage{threeparttable}\n",
    "\\usepackage{threeparttablex}\n",
    "\\usepackage[normalem]{ulem}\n",
    "\\usepackage{makecell}\n",
    "\\usepackage{xcolor}\n",
    "\\usepackage[margin=1in]{geometry}\n",
    "\\renewcommand{\\thetable}{S\\arabic{table}}\n",
    "\\usepackage{caption}\n",
    "\\captionsetup[table]{skip=10pt, font=bf}\n",
    "\\begin{document}\n",
    "\\thispagestyle{empty}\n",
    "\\begin{table}[H]\n",
    "\\centering\\renewcommand\\cellalign{lc}\n",
    "\\setcellgapes{3pt}\\makegapedcells\n",
    "\\centering\n",
    "\\caption{Changes in Outcomes Following Hope Group Participation, among Next-of-kin Caregivers in Colombia in 2024-2025}\n",
    "\\begin{threeparttable}\n",
    "\\resizebox*{!}{0.6\\textwidth}\n",
    "{\n",
    "\\small\n",
    "\\centering\n",
    paste0(latex_table1[1:5], collapse = "\n"),
    "\\textbf{Primary} & & & & & & \\\\ \n",
    paste0(latex_table1[6:12], collapse = "\n"),
    "\\midrule\\textbf{Secondary} & & & & & & \\\\ \n",
    paste0(latex_table2[6:9], collapse = "\n"),
    "\\multicolumn{7}{l}{$^\\dagger$ Unit of outcome: frequency of the two categories 'most of the time' and 'all of the time'.} \\\\ \n",    
    "\\multicolumn{7}{l}{$^\\ddagger$ Unit of outcome: mean days per week.} \\\\ \n",
    paste0(latex_table2[10], collapse = "\n"),
    "}\n", 
    "\\end{threeparttable}\n",
    "\\end{table}\n",
    "\\end{document}"
)

# Write LaTeX file
latex_file <- paste0(output_file_prefix, "_supp_table_1.tex")
writeLines(latex_doc, latex_file)

# Compile to PDF
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))  # Run twice for proper formatting

cat("\nSupplementary Table 1 saved to:\n")
cat("  CSV: ", paste0(output_file_prefix, "_supp_table_1.csv"), "\n")
cat("  LaTeX: ", latex_file, "\n")
cat("  PDF: ", paste0(output_file_prefix, "_supp_table_1.pdf"), "\n")

```

## Figure 2

```{r plot-main-figure-2, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
pos <- readRDS(paste0(output_file_prefix, "_primary_endpoints_grouped.rds"))

# Recode group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope and Resilience"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression and Anxiety']

# Plot A: Categorical mental health
tmp_cat <- subset(pos, item_type == "categorical" & group_label_long == "Caregiver Depression and Anxiety" & variable %in% c("bl", "el"))
tmp_cat[, time_label := ifelse(variable == "bl", "Baseline", "Endline")]
tmp_cat[, time_label := factor(time_label, levels = c("Baseline", "Endline"))]

# Get ratio data for labels
tmp_ratio_cat <- subset(pos, item_type == "categorical" & group_label_long == "Caregiver Depression and Anxiety" & variable == "ratio2")
tmp_ratio_cat[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
tmp_mean_cat <- tmp_cat[, list(y_pos = mean(median)), by = c("group_label_long")]
tmp_ratio_cat <- merge(tmp_ratio_cat, tmp_mean_cat, by = c("group_label_long"))
tmp_ratio_cat[, y_pos_adjusted := y_pos]

# Create plot A without faceting (or with fixed width)
plot_a <- ggplot(tmp_cat, aes(x = time_label, y = median)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(group = 1), linewidth = 1, color = "#E64B35FF") +
    geom_point(size = 2.5, color = "#E64B35FF") +
    geom_label(
        data = tmp_ratio_cat,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = seq(0, 1, 0.2), limits = c(0, 1), labels = scales::percent, expand = c(0,0)) +
    labs(
        x = "",
        y = "Frequency per week of categories\n'most of the time' + 'all of the time'"
    ) +
    facet_wrap(~ group_label_long, ncol = 2) +
    coord_cartesian(clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10, face = "bold"),
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    )

# Plot B: Out-of-7 items
tmp <- subset(pos, item_type == "out-of-7" & variable %in% c("bl", "el"))
tmp[, time_label := ifelse(variable == "bl", "Baseline", "Endline")]
tmp[, time_label := factor(time_label, levels = c("Baseline", "Endline"))]

# Recode item_high_label for display
tmp[, item_high_label := ifelse(item_high_label == "lower_is_better", "Negative outcomes improving", "Positive outcomes improving")]
tmp[, item_high_label := factor(item_high_label, levels = c("Positive outcomes improving", "Negative outcomes improving"))]

# Get ratio data for labels
tmp_ratio <- subset(pos, item_type == "out-of-7" & variable == "ratio2")
tmp_ratio[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
# Recode item_high_label for display in ratio data too
tmp_ratio[, item_high_label := ifelse(item_high_label == "lower_is_better", "Negative outcomes improving", "Positive outcomes improving")]
tmp_ratio[, item_high_label := factor(item_high_label, levels = c("Positive outcomes improving", "Negative outcomes improving"))]
tmp_mean <- tmp[, list(y_pos = mean(median)), by = c("group_label_long", "item_high_label")]
tmp_ratio <- merge(tmp_ratio, tmp_mean, by = c("group_label_long", "item_high_label"))
tmp_ratio[, y_pos_adjusted := y_pos]

# Create plot B
plot_b <- ggplot(tmp, aes(x = time_label, y = median, color = item_high_label)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(group = 1), linewidth = 1) +
    geom_point(size = 2.5) +
    geom_label(
        data = tmp_ratio,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        color = "black",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    facet_wrap(~ group_label_long, ncol = 2, scales = "free_y") +
    scale_color_npg(name = "Direction") +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = 0:7, expand = c(0,0)) +
    labs(
        x = "",
        y = "Mean days per week\n\n"
    ) +
    coord_cartesian(ylim = c(0, 7), clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10, face = "bold"),
        plot.title = element_text(face = "bold", size = 12),
        legend.position = "bottom",
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    ) +
    guides(color = guide_legend(nrow = 1))

# Create top row with plot_a on left and empty space on right
top_row <- plot_grid(plot_a, NULL, ncol = 2, 
    rel_widths = c(1.2, 1), labels = c("a", ""))
# Stack top row with plot_b that spans full width, with axis alignment
combined_plot <- plot_grid(top_row, plot_b, 
    ncol = 1, nrow = 2, rel_heights = c(0.8, 3), 
    labels = c("", "b"))


# Save combined plot
ggsave(
    filename = paste0(output_file_prefix, "_combined_figure_2.pdf"),
    plot = combined_plot,
    width = 10,
    height = 17,
    dpi = 300
)
```


## Supplementary Figure 2

```{r plot-figure-2, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=16}
pos <- readRDS(paste0(output_file_prefix, "_primary_endpoints_detailed.rds"))

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope and Resilience"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression and Anxiety']

# Plot A: Categorical mental health items
tmp_cat <- subset(pos, item_type == "categorical" & group_label_long == "Caregiver Depression and Anxiety" & variable %in% c("bl", "el"))
tmp_cat[, time_label := ifelse(variable == "bl", "Baseline", "Endline")]
tmp_cat[, time_label := factor(time_label, levels = c("Baseline", "Endline"))]

# Create facet label combining group and item
tmp_cat[, facet_label := paste0(group_label_long, "\n(", item_label_short, ")")]

# Get ratio data for labels and merge with median values for positioning
tmp_ratio_cat <- subset(pos, item_type == "categorical" & group_label_long == "Caregiver Depression and Anxiety" & variable == "ratio2")
tmp_ratio_cat[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
tmp_ratio_cat[, facet_label := paste0(group_label_long, "\n(", item_label_short, ")")]
# Get the mean of baseline and endline for each item to position the label
tmp_mean_cat <- tmp_cat[, list(y_pos = mean(median)), by = c("facet_label")]
tmp_ratio_cat <- merge(tmp_ratio_cat, tmp_mean_cat, by = c("facet_label"))
# Add vertical offset to prevent label overlap within each facet
tmp_ratio_cat <- tmp_ratio_cat[order(facet_label, y_pos)]
tmp_ratio_cat[, label_offset := 0]
tmp_ratio_cat[, y_pos_adjusted := y_pos + label_offset]

# Create plot A for categorical mental health
plot_a <- ggplot(tmp_cat, aes(x = time_label, y = median)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(group = 1), linewidth = 1, color = "#E64B35FF") +
    geom_point(size = 2.5, color = "#E64B35FF") +
    geom_label(
        data = tmp_ratio_cat,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = seq(0, 1, 0.2), limits = c(0, 1), labels = scales::percent) +
    labs(
        x = "",
        y = "Frequency per week of categories\n'most of the time' + 'all of the time'"
    ) +
    facet_wrap(~ facet_label, ncol = 3) +
    coord_cartesian(clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(face = "bold", size = 12),
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    )

# Plot B: Out-of-7 items
tmp <- subset(pos, item_type == "out-of-7" & variable %in% c("bl", "el"))
tmp[, time_label := ifelse(variable == "bl", "Baseline", "Endline")]
tmp[, time_label := factor(time_label, levels = c("Baseline", "Endline"))]

# Get ratio data for labels and merge with median values for positioning
tmp_ratio <- subset(pos, item_type == "out-of-7" & variable == "ratio2")
tmp_ratio[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
# Get the mean of baseline and endline for each item to position the label
tmp_mean <- tmp[, list(y_pos = mean(median)), by = c("item_label_short", "item_high_label", "group_label_long")]
tmp_ratio <- merge(tmp_ratio, tmp_mean, by = c("item_label_short", "item_high_label", "group_label_long"))
# Add vertical offset to prevent label overlap within facets
tmp_ratio <- tmp_ratio[order(group_label_long, y_pos)]
tmp_ratio[, label_offset := seq_len(.N) * 1.0 - mean(seq_len(.N) * 1.0), by = "group_label_long"]
tmp_ratio[, y_pos_adjusted := y_pos + label_offset]

# Create plot B
plot_b <- ggplot(tmp, aes(x = time_label, y = median, group = item_label_short, 
                     color = item_high_label)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(linetype = item_label_short), linewidth = 1) +
    geom_point(size = 2.5) +
    geom_text(
        data = subset(tmp, variable == "el"),
        aes(label = item_label_short),
        hjust = -0.3,
        size = 3,
        color = "black",
        show.legend = FALSE
    ) +
    geom_label(
        data = tmp_ratio,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        color = "black",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    facet_wrap(~ group_label_long, ncol = 3, scales = "free_y") +
    scale_color_npg(name = "Direction") +
    scale_linetype_discrete(guide = "none") +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = 0:7) +
    labs(
        x = "",
        y = "Mean days per week\n"
    ) +
    coord_cartesian(ylim = c(0, 7), clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10),
        plot.title = element_text(face = "bold", size = 12),
        legend.position = "bottom",
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    ) +
    guides(color = guide_legend(nrow = 1))

# Combine plots
combined_plot <- ggpubr::ggarrange(plot_a, plot_b, ncol = 1, nrow = 2, heights = c(1, 2), labels = c("a", "b"), align = "v")

# Save combined plot
ggsave(
    filename = paste0(output_file_prefix, "_combined_supp_figure_2.pdf"),
    plot = combined_plot,
    width = 10,
    height = 16,
    dpi = 300
)
```

# Session info
```{r session-info, include=TRUE, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
sessionInfo()
```
