---
title: "Colombia plots and tables for the Hope Groups paper - partial credit model v251224"
date: "2025-12-30"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

We found the PCM model (v251224) performed best on the Colombia data among the three IRT models considered (ordered logistic model, credit model, partial credit model). This vignette generates plots and tables for the Hope Groups paper using the partial credit model v251224.

# Standalone model fit

## Load/Install packages

```{r load-packages, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Install and load packages
packages <- c(
    "data.table",
    "here",
    "purrr",
    "formatR",
    "ggplot2",
    "ggsci",
    "hexbin",
    "bayesplot",
    "knitr",
    "kableExtra",
    "cmdstanr",
    "loo",
    "polycor",
    "GGally"
)
invisible(lapply(packages, library, character.only = TRUE))
```

```{r source-functions, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
source(here::here("R", "read_data_colombia.R"))
source(here::here("R", "train_test_split_data.R"))
source(here::here("R", "fit_credit_model.R"))
source(here::here("R", "fit_ordered_logit_model.R"))
source(here::here("R", "fit_partial_credit_model.R"))
```

## Data loading and pre-processing

```{r define-data-locations, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define directories
if (grepl("^/rds/general/user/or105", here::here())) {
    # Working on HPC
    on_hpc <- TRUE
    dir_data <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups/data"
    dir_out_base <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups"
} else {
    # Working locally
    on_hpc <- FALSE
    dir_data <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/data"
    dir_out_base <- "/Users/or105/sandbox"
}

# Define file names
file_data <- file.path(dir_data, "Colombia_data_baseline_endline_itemised_250927.csv")
file_data_quasi <- file.path(dir_data, "Colombia_data_quasi_assignments_250927.csv")

set.seed(42L)
seed <- c(123L)
```

```{r load-and-preprocess-data, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Read in data
tmp <- read_data_colombia(file_data)
dp <- copy(tmp$dp)
dit <- copy(tmp$dit)
dmeta <- copy(tmp$dmeta)

# Preprocess data
dp1 <- subset(dp, !grepl("agg", item_label))
dp1[, time := time + 1L]
dp1[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1$item_label)),
    time = unique(dp1$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1 <- merge(dp1, tmp, by = c("item_label", "time"))
setkey(dp1, pid, time, item_label)
dp1[, oid := .I]
setkey(dp1, oid)
tmp <- dp1[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1 <- merge(dp1, tmp, by = c("item_type", "oid"))
setkey(dp1, pid, time, item_label)
```

## Run partial credit model v251224

```{r setup-pcm-directories-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-251224")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix_pcm <- file.path(dir_out_pcm, "pcm_1")
```

```{r compile-stan-model-pcm-v251224, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "partial_credit_model_2cats_v251224.stan")
pcm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r pcm-fit-on-training-data-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
output_file_prefix <- file.path(dir_out_pcm, "pcm_1")
rds_file <- paste0(output_file_prefix, "_fit_alldata_stan.rds")
if (!file.exists(rds_file)) {
    cat("\n=== Running partial credit model v251224===\n")
    pcm_fit <-fit_partial_credit_model(
            dit,
            dp1,
            output_file_prefix = paste0(output_file_prefix, "_fit_alldata"),
            stan_file = here::here("src", "stan", "partial_credit_model_2cats_v251224.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 1000L,
            seed = seed,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
}
gc()
```

# Plots and Tables

## Create primary endpoints

Aggregate most + all of the time and compute mean for out-of-7

```{r colombia-endpoints, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, cache=TRUE}

# Aggregate categorical probabilities for most + all of the time
po <- pcm_fit$draws(
    variables = c("cat1_ordered_prob_by_obs"),
    inc_warmup = FALSE,
    format = "draws_df"
)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po[, y_stan := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\3", variable))]
po[, oidt := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\2", variable))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1[item_type == "categorical", ],
    select = c(oidt, pid, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("oidt"))
po <- subset(po, y_stan > 3)
po <- po[,
    list(y_stan = 45, prob = sum(prob)),
    by = c(".draw", "oidt", "pid", "item_label", "item_time_id", "item_type", "time_label")
]
po <- data.table::dcast(po,
    .draw + pid + item_type + item_label ~ time_label,
    value.var = "prob"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po[, diff := Baseline - Endline]
po[, ratio := 1 - Endline / Baseline]
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- po[,
    list(diff = mean(diff), ratio = mean(ratio), diff2 = mean(diff2), ratio2 = mean(ratio2), bl = mean(Baseline), el = mean(Endline)),
    by = c(".draw", "item_type", "item_label")
]
po <- melt(po,
    id.vars = c(".draw", "item_type", "item_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "bl", "el")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "item_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + item_label + variable ~ summary_name,
    value.var = "summary_value"
)
pos <- merge(pos, dit, by = c("item_type", "item_label"))
pos_cat1 <- copy(pos)
po <- NULL
gc()

# Compute mean for out-of-7 responses
po <- pcm_fit$draws(
    variables = c("cat2_ordered_prob_by_obs"),
    inc_warmup = FALSE,
    format = "draws_df"
)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po[, y_stan := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\3", variable))]
po[, oidt := as.integer(gsub("([a-z0-9_]+)\\[([0-9]+),([0-9]+)\\]", "\\2", variable))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1[item_type == "out-of-7", ],
    select = c(oidt, pid, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("oidt"))
po <- po[,
    list(mean = sum((y_stan - 1) * prob)),
    by = c(".draw", "oidt", "pid", "item_label", "item_time_id", "item_type", "time_label")
]
po <- data.table::dcast(po,
    .draw + pid + item_type + item_label ~ time_label,
    value.var = "mean"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po <- merge(po,
    subset(dit, select = c(item_type, item_label, item_high_label)),
    by = c("item_type", "item_label")
)
po[, diff := NA_real_]
po[, ratio := NA_real_]
tmp <- po[, which(item_high_label == "lower_is_better")]
set(po, tmp, "diff", po[tmp, Baseline - Endline])
set(po, tmp, "ratio", po[tmp, 1 - Endline / Baseline])
tmp <- po[, which(item_high_label == "higher_is_better")]
set(po, tmp, "diff", po[tmp, Endline - Baseline])
set(po, tmp, "ratio", po[tmp, Endline / Baseline - 1])
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- po[,
    list(diff = mean(diff), ratio = mean(ratio), diff2 = mean(diff2), ratio2 = mean(ratio2), bl = mean(Baseline), el = mean(Endline)),
    by = c(".draw", "item_type", "item_label", "item_high_label")
]
po <- melt(po,
    id.vars = c(".draw", "item_type", "item_label", "item_high_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "bl", "el")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "item_label", "item_high_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + item_label + item_high_label + variable ~ summary_name,
    value.var = "summary_value"
)
pos <- merge(pos, dit, by = c("item_type", "item_label", "item_high_label"))
pos_cat2 <- copy(pos)
po <- NULL
gc()

pos <- rbind(pos_cat1, pos_cat2, fill = TRUE)

cat("\nwrite endpoints to file=", paste0(output_file_prefix, "_primary_endpoints.rds"), "\n")
saveRDS(pos,
    file = paste0(output_file_prefix, "_primary_endpoints.rds"))
```

```{r load-endpoints, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, cache=TRUE}
pos <- readRDS(paste0(output_file_prefix, "_primary_endpoints.rds"))

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope and Resilience"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
```

## Figure 2

```{r plot-out-of-7-time-trends, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=8}
# Prepare data for plotting
tmp <- subset(pos, item_type == "out-of-7" & variable %in% c("bl", "el"))
tmp[, time_label := ifelse(variable == "bl", "Baseline", "Endline")]
tmp[, time_label := factor(time_label, levels = c("Baseline", "Endline"))]

# Get ratio data for labels and merge with median values for positioning
tmp_ratio <- subset(pos, item_type == "out-of-7" & variable == "ratio2")
tmp_ratio[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
# Get the mean of baseline and endline for each item to position the label
tmp_mean <- tmp[, list(y_pos = mean(median)), by = c("item_label_short", "item_high_label", "group_label_long")]
tmp_ratio <- merge(tmp_ratio, tmp_mean, by = c("item_label_short", "item_high_label", "group_label_long"))
# Add vertical offset to prevent label overlap within facets
tmp_ratio <- tmp_ratio[order(group_label_long, y_pos)]
tmp_ratio[, label_offset := seq_len(.N) * 1.0 - mean(seq_len(.N) * 1.0), by = "group_label_long"]
tmp_ratio[, y_pos_adjusted := y_pos + label_offset]

# Create plot with error bars and linetype for item_label_short
p <- ggplot(tmp, aes(x = time_label, y = median, group = item_label_short, 
                     color = item_high_label)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(linetype = item_label_short), linewidth = 1) +
    geom_point(size = 2.5) +
    geom_text(
        data = subset(tmp, variable == "el"),
        aes(label = item_label_short),
        hjust = -0.3,
        size = 3,
        show.legend = FALSE
    ) +
    geom_label(
        data = tmp_ratio,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    facet_wrap(~ group_label_long, ncol = 2, scales = "free_y") +
    scale_color_npg(name = "Direction") +
    scale_linetype_discrete(guide = "none") +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = 0:7) +
    labs(
        x = "",
        y = "Mean days per week\n"
    ) +
    coord_cartesian(ylim = c(0, 7), clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10),
        legend.position = "bottom",
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    ) +
    guides(color = guide_legend(nrow = 1))

# Save plot
ggsave(
    filename = paste0(output_file_prefix, "_out_of_7_time_trends.pdf"),
    plot = p,
    width = 10,
    height = 12,
    dpi = 300
)
```
# Session info
```{r session-info, include=TRUE, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
sessionInfo()
```
