---
title: "Colombia compare Likert outcome models"
date: "2025-12-26"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

In this analysis, we compare three different Item Response Theory (IRT) models fitted to survey data from the Hope Groups intervention in Colombia. All three models estimate an underlying latent construct (e.g., mental health status) from observed ordinal survey responses, with similar or even identical prior distributions on all parameters, but different likelihood constructions.

The data consist of Likert-scale survey items collected at baseline and endline, measuring parental responses to e.g. caregiver mental health, positive parenting behaviors, and child monitoring. We have two types of items: (1) categorical items with 5 ordered response categories (none of the time to all of the time), and (2) ordinal count items with 8 categories representing days per week (0-7 days). 

Our goal is to determine which statistical model best captures the structure of these ordinal responses.

# Different IRT Models

Throughout, let $i$ index participants ($i = 1, \ldots, n$), $j$ index items/questions ($j = 1, \ldots, J$), and $k$ index response categories ($k = 1, \ldots, K$). The subscript $ij$ denotes the response of participant $i$ to item $j$.

## Ordered Logistic Model
The first model that we considered is the widely used ordered logistic model, also called the graded response model. 

The ordered logistic model is specified in terms of cumulative probabilities:

\begin{align}
P(Y_{i,j} = k) &= P(Y_{i,j} \leq k) - P(Y_{i,j} \leq k-1) (\#eq:ordlog-response)\\
P(Y_{i,j} \leq k) &= \text{logit}^{-1}(\eta_{i,j} - c_{j,k}) (\#eq:ordlog-cumprob)\\
\eta_{i,j} &= \lambda_{j} \cdot \left(\theta_i + \mathbf{X}_{i,j}^T \boldsymbol{\beta}\right), (\#eq:ordlog-eta)
\end{align}

with the conventions that for $k=1$, $P(Y_{i,j} < 1) = 0$ and for $k=K$ $P(Y_{i,j} \leq K) = 1$. Here:

- $\theta_i$ is the skill (or latent factor) for participant $i$ ($i = 1, \ldots, n$)
- $\boldsymbol{\beta}$ are covariate effects (e.g., time effects) that modify the skill of each participant
- $\lambda_{j}$ are item loadings ($j = 1, \ldots, J$), that determine how the latent participant skills map to particular behaviours/items. The conceptual idea is that each item/response has its own "difficulty" or "discrimination" in relation to the latent trait. 
- $c_{j,k}$ must be ordered cutpoints for item $j$ and category $k$, with $c_{j,k} \geq c_{j,k-1}$. The idea is that when the item-specific skill $\eta_{i,j}$ exceeds the $k$th cutpoint, then the odds for responding in category $k$ or higher increases.

By construction, under the ordered logistic model, the cumulative log-odds are:

\begin{align}
\log \frac{\Pr(Y_{i,j} \leq k)}{1-\Pr(Y_{i,j} \leq k)}
= \eta_{i,j} - c_{j,k} (\#eq:cumlogodds)
\end{align}

Thus, the $\eta_{i,j}$ have a particular interpretation: when the item-specific skill of the $i$th participant $\eta_{i,j}$ equals $c_{j,k}$, then the odds that the $i$th participant responds at level $k$ or higher is $50-50$. When the the item-specific skill of the $i$th participant increases, the log-odds of responding in category $k$ or higher increases linearly.

The second important property of the ordered logistic model is that the model follows a proportional odds structure. When we compare two different values of the linear predictor, $\eta_1$ and $\eta_0$ (e.g., baseline vs. endline of the same participant on the same item, or two different participants on the same item), the difference in log-odds of being in category $k$ is:

\begin{align}
\log\frac{\Pr(Y \leq k \mid \eta_1)}{\Pr(Y > k \mid \eta_1)}
-
\log\frac{\Pr(Y \leq k \mid \eta_0)}{\Pr(Y > k \mid \eta_0)}
&= (\eta_1 - c_{j,k}) - (\eta_0 - c_{j,k}) (\#eq:propodd-1)\\
&= \eta_1 - \eta_0 (\#eq:propodd-2)
\end{align}

Thus, because the difference is constant across all categories $k$, the cumulative log-odds ratio that compares any two conditions is the same regardless of which category threshold we are considering. For example, when $\beta$ represents an intervention effect (e.g., $X_{i,j,t} = 1$ at time $t=1$ and $X_{i,j,t} = 0$ at time $t=0$), then 

\begin{align}
&\frac{\Pr(Y_{i,j,t=1} \leq k \mid \eta_{i,j,t=1})}{\Pr(Y_{i,j,t=1} > k \mid \eta_{i,j,t=1})} \bigg/
\frac{\Pr(Y_{i,j,t=0} \leq k \mid \eta_{i,j,t=0})}{\Pr(Y_{i,j,t=0} > k \mid \eta_{i,j,t=0})}\\
&\quad = 
\exp\Big( \lambda_j ( \theta_i + \beta ) - \lambda_j \theta_i  \Big)
= 
\exp( \lambda_j \beta ), (\#eq:propodd-3)
\end{align}

so when measured in cumulative odds, the effect of the intervention is proportional to $\exp\beta$, and the same regardless of the category $k$.

There are a few noteworthy details when implementing the ordered logistic model in a Bayesian framework. First, the likelihood is in Stan available in a slightly different form that uses the upper tail probabilities. Second, it is helpful to consider a non-centered parameterization for the latent traits, so that when the loadings are small, all corresponding cutpoints are automatically shrunk, and the sampler can more easily explore the posterior geometry. This leads to:

\begin{align}
P(Y_{i,j} = k) &= P(Y_{i,j} > k-1) - P(Y_{i,j} > k) (\#eq:ordlog-response-stan)\\
P(Y_{i,j} > k) &= \text{logit}^{-1}\Big(\phi_{i,j,k}\Big) (\#eq:ordlog-cumprob-stan)\\
\phi_{i,j,k} &= \lambda_{j} \cdot (\eta_{i,j} - c_{j,k}) (\#eq:ordlog-phi-stan)\\
\eta_{i,j} &= \theta_i + \mathbf{X}_{i,j}^T \boldsymbol{\beta}. (\#eq:ordlog-eta-stan)
\end{align}

Finally, we use the following prior distributions for all parameters:

\begin{align}
\theta_i &\sim \text{S2Z-Normal}(0, \sigma_{\theta}) (\#eq:ordlog-prior-theta)\\
\boldsymbol{\beta} &\sim \text{Normal}(0, 1) (\#eq:ordlog-prior-beta)\\
\lambda_{j} &\sim t_3^+(0, 1) \text{ for } j > 1 (\#eq:ordlog-prior-lambda)\\
c_{j,1} &\sim \text{Normal}(0, 3.5) (\#eq:ordlog-prior-c1)\\
c_{j,k} &= c_{j,1} + \sum_{\ell=1}^{k-1} \delta_{j,\ell} \text{ for } k > 1 (\#eq:ordlog-ck)\\
\delta_{j,\ell} &\sim \text{Normal}^+(0, 2.5) (\#eq:ordlog-prior-delta)
\end{align}

The S2Z-Normal (sum-to-zero) constraint ensures identifiability by forcing $\sum_{i=1}^n \theta_i = 0$ and adjusting the scale accordingly. The first loading $\lambda_1$ is fixed to 1 to set the scale of the latent trait and ensure multiplicative identifiability, as is standard in IRT models. All other loadsings are given half-t priors to allow for flexibility while preventing extreme values, again as is standard for Bayesian IRT models. The cutpoints $c_{j,k}$ are parameterized in an incremental approach, to ensure the required ordering.

## The Credit Model

The credit model, which is related to the widely used partial credit model in the educational literature, does not follow the cumulative approach of the ordered logistic model. Instead, it models the category probabilities more directly using a softmax function, and therefore tends to be a little faster to evaluate computationally. The model specification is: 

\begin{align}
P(Y_{ij} = k) &= \text{softmax}(\phi_{i,j,k}) = \frac{\exp(\phi_{i,j,k})}{\sum_{k'=1}^K \exp(\phi_{i,j,k'})} (\#eq:credit-response)\\
\phi_{i,j,1} &= 0\\
\phi_{i,j,k} &= \lambda_{j} \cdot \left(\theta_i + \mathbf{X}_{i,j}^T \boldsymbol{\beta} - c_{j,k}\right), \quad k=2,\dotsc,K(\#eq:credit-phi)
\end{align}

where the latent structure is exactly as for the Bayesian ordered logistic model. In our v251120 implementation, the priors are also as before, though in principle the cutpoints no longer have to be ordered.

The first observation is that for two categories ($K=2$), the above softmax construction equals

\begin{align}
P(Y_{ij} = 2) &= \frac{\exp\phi_{i,j,2}}{1 + \exp\phi_{i,j,2}} = \text{logit}^{-1}(\phi_{i,j,2}), (\#eq:credit-phi)
\end{align}

and so the credit model and the ordered logistic model are equivalent for binary data.


\begin{align}
\frac{\Pr(Y_{i,j,t=1} = k \mid \eta_{i,j,t=1})}{\Pr(Y_{i,j,t=0} = k \mid \eta_{i,j,t=0})}
= 
\exp\Big( \lambda_j ( \theta_i + \beta ) - \lambda_j \theta_i  \Big)
= 
\exp( \lambda_j \beta ), (\#eq:propodd-3)
\end{align}

# Model comparison on the Colombia data

# Install packages

```{r load-packages, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Install and load packages
packages <- c(
    "data.table",
    "here",
    "purrr",
    "ggplot2",
    "ggsci",
    "hexbin",
    "bayesplot",
    "knitr",
    "kableExtra",
    "cmdstanr",
    "loo",
    "polycor",
    "GGally"
)
invisible(lapply(packages, library, character.only = TRUE))
```

```{r source-functions, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
source(here::here("R", "read_data_colombia.R"))
source(here::here("R", "train_test_split_data.R"))
source(here::here("R", "credit_model_run_analysis.R"))
source(here::here("R", "ordered_logit_model_run_analysis.R"))
source(here::here("R", "partial_credit_model_run_analysis.R"))
```

# Data loading and pre-processing

```{r define-data-locations, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define directories
if (grepl("^/rds/general/user/or105", here::here())) {
    # Working on HPC
    on_hpc <- TRUE
    dir_data <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups/data"
    dir_out_base <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups"
} else {
    # Working locally
    on_hpc <- FALSE
    dir_data <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/data"
    dir_out_base <- "/Users/or105/sandbox"
}

# Define file names
file_data <- file.path(dir_data, "Colombia_data_baseline_endline_itemised_250927.csv")
file_data_quasi <- file.path(dir_data, "Colombia_data_quasi_assignments_250927.csv")

set.seed(42L)

# Define seeds for multiple runs
seeds <- c(123L, 456L, 789L, 1011L, 1213L, 1415L, 1617L, 1819L, 2021L, 2223L)
```

```{r load-and-preprocess-data, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Read in data
tmp <- read_data_colombia(file_data)
dp <- copy(tmp$dp)
dit <- copy(tmp$dit)
dmeta <- copy(tmp$dmeta)

# Preprocess data
dp1 <- subset(dp, !grepl("agg", item_label))
dp1[, time := time + 1L]
dp1[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1$item_label)),
    time = unique(dp1$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1 <- merge(dp1, tmp, by = c("item_label", "time"))
setkey(dp1, pid, time, item_label)
dp1[, oid := .I]
setkey(dp1, oid)
tmp <- dp1[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1 <- merge(dp1, tmp, by = c("item_type", "oid"))
setkey(dp1, pid, time, item_label)
```

# Run ordered logistic model with 2 categories

```{r setup-ordlog-directories, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define ordered logistic output directories
dir_out <- file.path(dir_out_base, "colombia-run-orderedlogistic-251222b")
dir_logs <- file.path(dir_out, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out)) {
    dir.create(dir_out, recursive = TRUE)
}
if (!dir.exists(dir_logs)) {
    dir.create(dir_logs, recursive = TRUE)
}

output_file_prefix <- file.path(dir_out, "ordlog_1")
```

```{r compile-stan-model, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "ordered_logit_2cats_v251222.stan")
ol_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE)
    )
```

```{r fit-on-training-data, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Run with 10 different seeds
for (seed in seeds) {
    seed_dir <- file.path(dir_out, paste0('seed-', seed))
    dir.create(seed_dir, recursive = TRUE, showWarnings = FALSE)
    output_file_prefix_seed <- file.path(seed_dir, "ordlog_1")
    rds_file <- paste0(output_file_prefix_seed, "_fit_alldata_stan.rds")
    if (!file.exists(rds_file)) {
        cat("\n=== Running ordered logit model with seed", seed, "===\n")
        ordered_logit_model_run_analysis(
            dit,
            dp1,
            output_file_prefix = paste0(output_file_prefix_seed, "_fit_alldata"),
            stan_file = here::here("src", "stan", "ordered_logit_2cats_v251222.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 500L,
            seed = seed,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
    }
    gc()
}
```

# Run credit model with 2 categories version credit_model_2cats_v251223

```{r setup-creditmodel-directories-v251223, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define credit model output directories
dir_out_cm <- file.path(dir_out_base, "colombia-run-creditmodel-251223")
dir_logs_cm <- file.path(dir_out_cm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_cm)) {
    dir.create(dir_out_cm, recursive = TRUE)
}
if (!dir.exists(dir_logs_cm)) {
    dir.create(dir_logs_cm, recursive = TRUE)
}

output_file_prefix_cm <- file.path(dir_out_cm, "cm_2")
```

```{r compile-stan-model-v251223, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "credit_model_2cats_v251223.stan")
cm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE)
    )
```

```{r cm-fit-on-training-data-v251223, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Run with 10 different seeds
for (seed in seeds) {
    seed_dir <- file.path(dir_out_cm, paste0('seed-', seed))
    dir.create(seed_dir, recursive = TRUE, showWarnings = FALSE)
    output_file_prefix_seed <- file.path(seed_dir, "cm_2")
    rds_file <- paste0(output_file_prefix_seed, "_fit_alldata_stan.rds")
    if (!file.exists(rds_file)) {
        cat("\n=== Running credit model v251223 with seed", seed, "===\n")
        credit_model_run_analysis(
            dit,
            dp1,
            output_file_prefix = paste0(output_file_prefix_seed, "_fit_alldata"),
            stan_file = here::here("src", "stan", "credit_model_2cats_v251223.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 500L,
            seed = seed,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
    }
    gc()
}
```

# Run credit model with 2 categories version credit_model_2cats_v251224

```{r setup-creditmodel-directories-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define credit model output directories
dir_out_cm <- file.path(dir_out_base, "colombia-run-creditmodel-251224")
dir_logs_cm <- file.path(dir_out_cm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_cm)) {
    dir.create(dir_out_cm, recursive = TRUE)
}
if (!dir.exists(dir_logs_cm)) {
    dir.create(dir_logs_cm, recursive = TRUE)
}

output_file_prefix_cm <- file.path(dir_out_cm, "cm_3")
```

```{r compile-stan-model-3, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "credit_model_2cats_v251224.stan")
cm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r cm-fit-on-training-data-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Run with 10 different seeds
for (seed in seeds) {
    seed_dir <- file.path(dir_out_cm, paste0('seed-', seed))
    dir.create(seed_dir, recursive = TRUE, showWarnings = FALSE)
    output_file_prefix_seed <- file.path(seed_dir, "cm_3")
    rds_file <- paste0(output_file_prefix_seed, "_fit_alldata_stan.rds")
    if (!file.exists(rds_file)) {
        cat("\n=== Running credit model v251224 with seed", seed, "===\n")
        credit_model_run_analysis(
            dit,
            dp1,
            output_file_prefix = paste0(output_file_prefix_seed, "_fit_alldata"),
            stan_file = here::here("src", "stan", "credit_model_2cats_v251224.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 500L,
            seed = seed,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
    }
    gc()
}
```

# Run partial credit model with 2 categories version partial_credit_model_2cats_v251224

```{r setup-pcm-directories-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-run-partialcreditmodel-251224")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix_pcm <- file.path(dir_out_pcm, "pcm_1")
```

```{r compile-stan-model-pcm-v251224, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "partial_credit_model_2cats_v251224.stan")
pcm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r pcm-fit-on-training-data-v251224, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Run with 10 different seeds
for (seed in seeds) {
    seed_dir <- file.path(dir_out_pcm, paste0('seed-', seed))
    dir.create(seed_dir, recursive = TRUE, showWarnings = FALSE)
    output_file_prefix_seed <- file.path(seed_dir, "pcm_1")
    rds_file <- paste0(output_file_prefix_seed, "_fit_alldata_stan.rds")
    if (!file.exists(rds_file)) {
        cat("\n=== Running partial credit model v251224 with seed", seed, "===\n")
        partial_credit_model_run_analysis(
            dit,
            dp1,
            output_file_prefix = paste0(output_file_prefix_seed, "_fit_alldata"),
            stan_file = here::here("src", "stan", "partial_credit_model_2cats_v251224.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 500L,
            seed = seed,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
    }
    gc()
}
```

# Model Comparison

We now compare the three models using Leave-One-Out Cross-Validation (LOO) via the Expected Log Predictive Density (ELPD). The LOO-ELPD provides an estimate of out-of-sample predictive performance, with higher (less negative) values indicating better predictive accuracy.

```{r model-comparison-loo, include=FALSE, eval=FALSE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
if(!file.exists(file.path(dir_out_base, "colombia-run-creditmodel-251224", "colombia_model_comparison_2cat.csv"))) {
  # Process models for each seed sequentially
  for (seed in seeds) {
    cat("\n=== Processing seed", seed, "===\n")
    
    # Define file paths for this seed
    ol_rds <- file.path(dir_out_base, "colombia-run-orderedlogistic-251222b", 
                        paste0("seed-", seed), "ordlog_1_fit_alldata_stan.rds")
    cm_v251223_rds <- file.path(dir_out_base, "colombia-run-creditmodel-251223",
                                paste0("seed-", seed), "cm_2_fit_alldata_stan.rds")
    cm_v251224_rds <- file.path(dir_out_base, "colombia-run-creditmodel-251224",
                                paste0("seed-", seed), "cm_3_fit_alldata_stan.rds")
    pcm_v251224_rds <- file.path(dir_out_base, "colombia-run-partialcreditmodel-251224",
                                 paste0("seed-", seed), "pcm_1_fit_alldata_stan.rds")
    
    # Process ordered logit model
    cat("  --- Evaluating ordered logit model ---\n")
    ol_fit <- readRDS(ol_rds)
    log_lik_ol <- ol_fit$draws("log_lik", format = "matrix")
    loo_ol <- loo::loo(log_lik_ol)
    waic_ol <- loo::waic(log_lik_ol)
    ol_fit <- NULL
    log_lik_ol <- NULL
    gc()
    
    # Process credit model v251223
    cat("  --- Evaluating credit model v251223 ---\n")
    cm_fit_v251223 <- readRDS(cm_v251223_rds)
    log_lik_cm_v251223 <- cm_fit_v251223$draws("log_lik", format = "matrix")
    loo_cm_v251223 <- loo::loo(log_lik_cm_v251223)
    waic_cm_v251223 <- loo::waic(log_lik_cm_v251223)
    cm_fit_v251223 <- NULL
    log_lik_cm_v251223 <- NULL
    gc()
    
    # Process credit model v251224
    cat("  --- Evaluating credit model v251224 ---\n")
    cm_fit_v251224 <- readRDS(cm_v251224_rds)
    log_lik_cm_v251224 <- cm_fit_v251224$draws("log_lik", format = "matrix")
    loo_cm_v251224 <- loo::loo(log_lik_cm_v251224)
    waic_cm_v251224 <- loo::waic(log_lik_cm_v251224)
    cm_fit_v251224 <- NULL
    log_lik_cm_v251224 <- NULL
    gc()
    
    # Process partial credit model v251224
    cat("  --- Evaluating partial credit model v251224 ---\n")
    pcm_fit_v251224 <- readRDS(pcm_v251224_rds)
    log_lik_pcm_v251224 <- pcm_fit_v251224$draws("log_lik", format = "matrix")
    loo_pcm_v251224 <- loo::loo(log_lik_pcm_v251224)
    waic_pcm_v251224 <- loo::waic(log_lik_pcm_v251224)
    pcm_fit_v251224 <- NULL
    log_lik_pcm_v251224 <- NULL
    gc()
    
    # Load convergence diagnostics
    cat("  --- Loading convergence diagnostics ---\n")
    conv_ol <- fread(file.path(dir_out_base, "colombia-run-orderedlogistic-251222b",
                                paste0("seed-", seed), "ordlog_1_fit_alldata_convergence_mixing.csv"))
    conv_cm_v251223 <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251223",
                                        paste0("seed-", seed), "cm_2_fit_alldata_convergence_mixing.csv"))
    conv_cm_v251224 <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251224",
                                        paste0("seed-", seed), "cm_3_fit_alldata_convergence_mixing.csv"))
    conv_pcm_v251224 <- fread(file.path(dir_out_base, "colombia-run-partialcreditmodel-251224",
                                         paste0("seed-", seed), "pcm_1_fit_alldata_convergence_mixing.csv"))
    
    # Load timing data
    cat("  --- Loading timing data ---\n")
    timing_ol <- fread(file.path(dir_out_base, "colombia-run-orderedlogistic-251222b",
                                  paste0("seed-", seed), "ordlog_1_fit_alldata_timing.csv"))
    timing_cm_v251223 <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251223",
                                          paste0("seed-", seed), "cm_2_fit_alldata_timing.csv"))
    timing_cm_v251224 <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251224",
                                          paste0("seed-", seed), "cm_3_fit_alldata_timing.csv"))
    timing_pcm_v251224 <- fread(file.path(dir_out_base, "colombia-run-partialcreditmodel-251224",
                                           paste0("seed-", seed), "pcm_1_fit_alldata_timing.csv"))
    
    # Load Brier scores
    cat("  --- Loading Brier scores ---\n")
    brier_ol <- fread(file.path(dir_out_base, "colombia-run-orderedlogistic-251222b",
                                 paste0("seed-", seed), "ordlog_1_fit_alldata_ordered_brierscore.csv"))
    brier_cm_v251223 <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251223",
                                         paste0("seed-", seed), "cm_2_fit_alldata_ordered_brierscore.csv"))
    brier_cm_v251224 <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251224",
                                         paste0("seed-", seed), "cm_3_fit_alldata_ordered_brierscore.csv"))
    brier_pcm_v251224 <- fread(file.path(dir_out_base, "colombia-run-partialcreditmodel-251224",
                                          paste0("seed-", seed), "pcm_1_fit_alldata_ordered_brierscore.csv"))
    
    # Add model identifier to each Brier score dataset
    brier_ol[, Model := "Ordered Logistic (v251222)"]
    brier_cm_v251223[, Model := "Credit Model (v251223)"]
    brier_cm_v251224[, Model := "Credit Model (v251224)"]
    brier_pcm_v251224[, Model := "Partial Credit Model (v251224)"]
    
    # Combine all Brier scores for this seed
    brier_seed <- rbindlist(list(brier_ol, brier_cm_v251223, brier_cm_v251224, brier_pcm_v251224))
    brier_seed[, seed := seed]
    
    # Save question-level Brier scores
    fwrite(brier_seed,
           file = file.path(dir_out_base, "colombia-run-creditmodel-251224",
                           paste0("colombia_brier_scores_by_question_seed", seed, ".csv")))
    
    # Compute mean Brier score across questions for comparison table
    brier_summary <- brier_seed[, list(
      mean_brier_cat = mean(median[item_type == "categorical"]),
      mean_brier_out7 = mean(median[item_type == "out-of-7"]),
      mean_brier_all = mean(median)
    ), by = Model]
    
    # Create comparison table for this seed
    comparison_seed <- data.table(
      seed = seed,
      Model = c("Ordered Logistic (v251222)", 
                "Credit Model (v251223)", "Credit Model (v251224)", 
                "Partial Credit Model (v251224)"),
      ELPD_loo = c(loo_ol$estimates["elpd_loo", "Estimate"],
                   loo_cm_v251223$estimates["elpd_loo", "Estimate"],
                   loo_cm_v251224$estimates["elpd_loo", "Estimate"],
                   loo_pcm_v251224$estimates["elpd_loo", "Estimate"]),
      ELPD_loo_SE = c(loo_ol$estimates["elpd_loo", "SE"],
                      loo_cm_v251223$estimates["elpd_loo", "SE"],
                      loo_cm_v251224$estimates["elpd_loo", "SE"],
                      loo_pcm_v251224$estimates["elpd_loo", "SE"]),
      WAIC = c(waic_ol$estimates["elpd_waic", "Estimate"],
               waic_cm_v251223$estimates["elpd_waic", "Estimate"],
               waic_cm_v251224$estimates["elpd_waic", "Estimate"],
               waic_pcm_v251224$estimates["elpd_waic", "Estimate"]),
      WAIC_SE = c(waic_ol$estimates["elpd_waic", "SE"],
                  waic_cm_v251223$estimates["elpd_waic", "SE"],
                  waic_cm_v251224$estimates["elpd_waic", "SE"],
                  waic_pcm_v251224$estimates["elpd_waic", "SE"]),
      min_ess_bulk = c(min(conv_ol$ess_bulk, na.rm = TRUE),
                       min(conv_cm_v251223$ess_bulk, na.rm = TRUE),
                       min(conv_cm_v251224$ess_bulk, na.rm = TRUE),
                       min(conv_pcm_v251224$ess_bulk, na.rm = TRUE)),
      min_ess_tail = c(min(conv_ol$ess_tail, na.rm = TRUE),
                       min(conv_cm_v251223$ess_tail, na.rm = TRUE),
                       min(conv_cm_v251224$ess_tail, na.rm = TRUE),
                       min(conv_pcm_v251224$ess_tail, na.rm = TRUE)),
      max_rhat = c(max(conv_ol$rhat, na.rm = TRUE),
                   max(conv_cm_v251223$rhat, na.rm = TRUE),
                   max(conv_cm_v251224$rhat, na.rm = TRUE),
                   max(conv_pcm_v251224$rhat, na.rm = TRUE)),
      max_total_chain_minutes = c(max(timing_ol$total_chain_minutes, na.rm = TRUE),
                                  max(timing_cm_v251223$total_chain_minutes, na.rm = TRUE),
                                  max(timing_cm_v251224$total_chain_minutes, na.rm = TRUE),
                                  max(timing_pcm_v251224$total_chain_minutes, na.rm = TRUE))
    )
    
    # Merge Brier scores into comparison table
    comparison_seed <- merge(comparison_seed, brier_summary, by = "Model")
    
    # Append to file
    fwrite(comparison_seed,
           file = file.path(dir_out_base, "colombia-run-creditmodel-251224", 
                           paste0("colombia_model_comparison_2cat_seed", seed, ".csv")))
    
    # Clear variables and run gc
    loo_ol <- waic_ol <- conv_ol <- timing_ol <- brier_ol <- NULL
    loo_cm_v251223 <- waic_cm_v251223 <- conv_cm_v251223 <- timing_cm_v251223 <- brier_cm_v251223 <- NULL
    loo_cm_v251224 <- waic_cm_v251224 <- conv_cm_v251224 <- timing_cm_v251224 <- brier_cm_v251224 <- NULL
    loo_pcm_v251224 <- waic_pcm_v251224 <- conv_pcm_v251224 <- timing_pcm_v251224 <- brier_pcm_v251224 <- NULL
    brier_seed <- brier_summary <- comparison_seed <- NULL
    gc()
  }
  
  # Aggregate results across seeds
  cat("\n=== Aggregating results across seeds ===\n")
  comparison_all <- rbindlist(lapply(seeds, function(seed) {
    fread(file.path(dir_out_base, "colombia-run-creditmodel-251224",
                   paste0("colombia_model_comparison_2cat_seed", seed, ".csv")))
  }))
  
  # Compute summary statistics across seeds
  comparison_dt <- comparison_all[,
    list(
      ELPD_loo = mean(ELPD_loo),
      ELPD_loo_SE = mean(ELPD_loo_SE),
      WAIC = mean(WAIC),
      WAIC_SE = mean(WAIC_SE),
      min_ess_bulk = mean(min_ess_bulk),
      min_ess_tail = mean(min_ess_tail),
      max_rhat = mean(max_rhat),
      max_total_chain_minutes = mean(max_total_chain_minutes),
      mean_brier_cat = mean(mean_brier_cat),
      mean_brier_out7 = mean(mean_brier_out7),
      mean_brier_all = mean(mean_brier_all)
    ),
    by = Model
  ]
  
  # Round for display
  comparison_dt[, ELPD_loo := round(ELPD_loo, 1)]
  comparison_dt[, ELPD_loo_SE := round(ELPD_loo_SE, 1)]
  comparison_dt[, WAIC := round(WAIC, 1)]
  comparison_dt[, WAIC_SE := round(WAIC_SE, 1)]
  comparison_dt[, min_ess_bulk := round(min_ess_bulk, 0)]
  comparison_dt[, min_ess_tail := round(min_ess_tail, 0)]
  comparison_dt[, max_rhat := round(max_rhat, 3)]
  comparison_dt[, max_total_chain_minutes := round(max_total_chain_minutes, 2)]
  comparison_dt[, mean_brier_cat := round(mean_brier_cat, 4)]
  comparison_dt[, mean_brier_out7 := round(mean_brier_out7, 4)]
  comparison_dt[, mean_brier_all := round(mean_brier_all, 4)]
  
  fwrite(comparison_dt, 
         file = file.path(dir_out_base, "colombia-run-creditmodel-251224", "colombia_model_comparison_2cat.csv"))
} else {
  comparison_dt <- fread(file.path(dir_out_base, "colombia-run-creditmodel-251224", "colombia_model_comparison_2cat.csv"))
}

# Create a nice table for display
knitr::kable(comparison_dt, 
             caption = "Extended Model Comparison Metrics",
             col.names = c("Model", "ELPD (LOO)", "SE", "WAIC", "SE",
                           "Min ESS (bulk)", "Min ESS (tail)", 
                           "Max Rhat", "Max Chain Time (min)",
                           "Brier (Cat)", "Brier (Out7)", "Brier (All)")) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
cat("\n\nInterpretation:\n")
cat("- ELPD (LOO) & WAIC: Higher (less negative) is better\n")
cat("- Min ESS: Should be > 400 for reliable inference (we ran 2000 samples across 4 chains)\n")
cat("- Max Rhat: Should be < 1.01 for convergence\n")
cat("- Max Chain Time: Computational efficiency\n")
cat("- Brier Scores: Lower is better (0 = perfect predictions, 1 = worst). Shown separately for categorical items, out-of-7 items, and overall.\n")
```

The `loo_compare` output shows models ranked by ELPD (best model first). The `elpd_diff` column shows the difference in ELPD from the best model, and `se_diff` provides the standard error of this difference. A difference greater than 2 standard errors suggests meaningful improvement in predictive performance.

# Session info
```{r session-info, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
sessionInfo()
```
