---
title: "Investigate ADVI vs HMC for ordered logit model on Colombia data"
date: "2026-04-30"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This vignette applies the ordered logit model (ncats v260413) to the Colombia data for comparison with other IRT models. It generates plots and tables for the Hope Groups paper using the ordered logit model v260413.

# Standalone model fit

## Load/Install packages

```{r load-packages, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Install and load packages
packages <- c(
    "cowplot",
    "data.table",
    "here",
    "purrr",
    "formatR",
    "ggplot2",
    "ggsci",
    "ggpubr",
    "hexbin",
    "bayesplot",
    "knitr",
    "kableExtra",
    "cmdstanr",
    "loo",
    "polycor",
    "GGally",
    "MatchIt",
    "posterior"
)

# install.packages("remotes")  # if you don’t already have it
# remotes::install_github("stan-dev/cmdstanr") # if you don’t already have it

invisible(lapply(packages, function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}))

```

```{r source-functions, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
source(here::here("R", "read_data_colombia.R"))
source(here::here("R", "read_data_ukraine.R"))
source(here::here("R", "train_test_split_data.R"))
source(here::here("R", "fit_ordered_logit_model_ncats.R"))
source(here::here("R", "fit_ordered_logit_model_ncats_advi.R"))
source(here::here("R", "get_endpoints.R"))
```

## Run ordered logit model v260413 on Colombia data (vanilla)

```{r define-data-locations-260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define directories
if (grepl("^/rds/general/user/or105", here::here())) {
    # Working on HPC
    on_hpc <- TRUE
    dir_data <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups/data"
    dir_out_base <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups"
} else {
    # Working locally
    on_hpc <- FALSE
    dir_data <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/data"
    dir_out_base <- "/Users/or105/sandbox"
}

# Define file names
file_data <- file.path(dir_data, "Colombia_data_baseline_endline_itemised_250927.csv")
file_data_quasi <- file.path(dir_data, "Colombia_data_quasi_assignments_250927.csv")

set.seed(42L)
seed <- c(123L)
```

```{r load-and-preprocess-data-colombia-260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Read in data from Colombia
tmp <- read_data_colombia(file_data)
dp_col <- copy(tmp$dp)
dit_col <- copy(tmp$dit)
dmeta_col <- copy(tmp$dmeta)

# Preprocess data
dp1_col <- subset(dp_col, !grepl("agg", item_label))
dp1_col[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1_col$item_label)),
    time = unique(dp1_col$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1_col <- merge(dp1_col, tmp, by = c("item_label", "time"))
dp1_col <- merge(dp1_col, unique(subset(dit_col, select = c(item_type, item_type_id))), by = "item_type")
setkey(dp1_col, item_type_id, pid, time, item_label)
dp1_col[, oid := .I]
setkey(dp1_col, oid)
tmp <- dp1_col[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1_col <- merge(dp1_col, tmp, by = c("item_type", "oid"))

setkey(dp1_col, pid, time, item_label)
```

```{r setup-ol-directories-v260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define ordered logit model output directories
dir_out_ol <- "/Users/or105/sandbox/colombia-ordered_logit-260430-vanilla-advi-vs-hmc"
dir_logs_ol <- file.path(dir_out_ol, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_ol)) {
    dir.create(dir_out_ol, recursive = TRUE)
}
if (!dir.exists(dir_logs_ol)) {
    dir.create(dir_logs_ol, recursive = TRUE)
}

output_file_prefix_hmc <- file.path(dir_out_ol, "ol_1_hmc")
output_file_prefix_advi <- file.path(dir_out_ol, "ol_1_advi")

# Save data for later use
data_file <- file.path(dir_out_ol, "ol_1_hmc_data.rds")
if (!file.exists(data_file)) {
    saveRDS(list(dp1 = dp1_col, dit = dit_col), file = data_file)
    cat("Saved data to:", data_file, "\n")
}
```

```{r compile-stan-model-ol-v260413-vanilla, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "ordered_logit_ncats_v260413.stan")
ol_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r ol-fit-colombia-data-vanilla-hmc, include=TRUE, eval=FALSE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
fit_ordered_logit_model_ncats(
            dit_col,
            dp1_col,
            output_file_prefix = output_file_prefix_hmc,
            stan_file = here::here("src", "stan", "ordered_logit_ncats_v260413.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 1000L,
            seed = seed,
            x_formula = ~ time - 1,
            resume = TRUE,
            with_core_analyses = FALSE,
            with_additional_analyses = FALSE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
gc()
```

## Run ordered logit model v260413 on Colombia data using ADVI

```{r ol-fit-colombia-data-vanilla-advi, include=TRUE, eval=FALSE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
fit_ordered_logit_model_ncats_advi(
            dit_col,
            dp1_col,
            output_file_prefix = output_file_prefix_advi,
            stan_file = here::here("src", "stan", "ordered_logit_ncats_v260413.stan"),
            iter = 10000L,
            grad_samples = 1L,
            elbo_samples = 100L,
            output_samples = 4000L,
            seed = seed,
            x_formula = ~ time - 1,
            resume = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
gc()
```

# Compare HMC vs ADVI

## Load results

```{r load-results, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Load draws from both methods
draws_hmc <- readRDS(paste0(output_file_prefix_hmc, "_draws.rds"))
draws_advi <- readRDS(paste0(output_file_prefix_advi, "_draws.rds"))

# Convert to data.table format for easier manipulation
require(posterior)
require(data.table)

df_hmc <- as_draws_df(draws_hmc)
df_advi <- as_draws_df(draws_advi)

cat("HMC draws:", nrow(df_hmc), "samples\n")
cat("ADVI draws:", nrow(df_advi), "samples\n")
```

## Compare effect size estimates for each survey item 

```{r compare-endpoints, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Load data
tmp <- readRDS(paste0(output_file_prefix_hmc, "_data.rds"))
dp1 <- copy(tmp$dp1)
dit <- copy(tmp$dit)

cat("\nCalling get_endpoints for HMC...\n")
# Get endpoints using the function for HMC
endpoints_hmc <- get_endpoints(
    dp1 = dp1,
    dit = dit,
    draws_file = paste0(output_file_prefix_hmc, "_draws.rds"),
    categorical_threshold = 3,
    endpoint_type = "items"
)

cat("\nget_endpoints returned successfully\n")
cat("Class:", class(endpoints_hmc), "\n")
cat("Dimensions:", dim(endpoints_hmc), "\n")
cat("Column names:", paste(names(endpoints_hmc), collapse = ", "), "\n")
cat("First few rows:\n")
print(head(endpoints_hmc, 3))

endpoints_hmc[, method := "HMC"]

# Get endpoints using the function for ADVI
endpoints_advi <- get_endpoints(
    dp1 = dp1,
    dit = dit,
    draws_file = paste0(output_file_prefix_advi, "_draws.rds"),
    categorical_threshold = 3,
    endpoint_type = "items"
)
endpoints_advi[, method := "ADVI"]

# Check what columns we have
cat("\nColumns in endpoints_hmc:\n")
print(names(endpoints_hmc))
cat("\nFirst few rows:\n")
print(head(endpoints_hmc))

# Merge HMC and ADVI results for comparison
# Both datasets contain categorical items (with item_time_id) and out-of-7 items (without)
# Use all common columns for merging
common_cols <- intersect(names(endpoints_hmc), names(endpoints_advi))
common_cols <- setdiff(common_cols, "method")  # Remove method column
cat("\nCommon columns for comparison:\n")
print(common_cols)

# For merging, we need unique identifiers
# Categorical items: item_type, item_label, item_time_id, variable
# Out-of-7 items: item_type, item_label, variable (no item_time_id)
# We'll create a unique ID that handles both cases

endpoints_hmc_copy <- copy(endpoints_hmc)
endpoints_advi_copy <- copy(endpoints_advi)

# Create unique ID for merging
if ("item_time_id" %in% names(endpoints_hmc_copy)) {
    endpoints_hmc_copy[, merge_id := paste(item_type, item_label, 
                                            ifelse(is.na(item_time_id), "NA", as.character(item_time_id)), 
                                            variable, sep = "___")]
    endpoints_advi_copy[, merge_id := paste(item_type, item_label,
                                             ifelse(is.na(item_time_id), "NA", as.character(item_time_id)),
                                             variable, sep = "___")]
} else {
    endpoints_hmc_copy[, merge_id := paste(item_type, item_label, variable, sep = "___")]
    endpoints_advi_copy[, merge_id := paste(item_type, item_label, variable, sep = "___")]
}

# Select quantile columns and merge_id
quant_cols_hmc <- endpoints_hmc_copy[, .(merge_id, q_lower, iqr_lower, median, iqr_upper, q_upper)]
setnames(quant_cols_hmc, 
         c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper"),
         c("q_lower_hmc", "iqr_lower_hmc", "median_hmc", "iqr_upper_hmc", "q_upper_hmc"))

quant_cols_advi <- endpoints_advi_copy[, .(merge_id, q_lower, iqr_lower, median, iqr_upper, q_upper)]
setnames(quant_cols_advi,
         c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper"),
         c("q_lower_advi", "iqr_lower_advi", "median_advi", "iqr_upper_advi", "q_upper_advi"))

# Merge
endpoints_comparison <- merge(quant_cols_hmc, quant_cols_advi, by = "merge_id")

# Add back metadata from HMC (they should be identical for both)
meta_cols <- setdiff(names(endpoints_hmc), c("method", "q_lower", "iqr_lower", "median", "iqr_upper", "q_upper"))
endpoints_hmc_copy[, merge_id := paste(item_type, item_label,
                                        ifelse("item_time_id" %in% names(endpoints_hmc_copy) & !is.na(item_time_id), 
                                               as.character(item_time_id), "NA"),
                                        variable, sep = "___")]
meta_data <- unique(endpoints_hmc_copy[, c("merge_id", ..meta_cols)])
endpoints_comparison <- merge(endpoints_comparison, meta_data, by = "merge_id")

# Compute difference in medians
endpoints_comparison[, median_diff := median_hmc - median_advi]
endpoints_comparison[, abs_median_diff := abs(median_diff)]

# Order by absolute difference
setorder(endpoints_comparison, -abs_median_diff)

# Save to CSV
fwrite(
    endpoints_comparison,
    file = file.path(dir_out_ol, "endpoints_comparison_hmc_vs_advi.csv")
)
cat("\nSaved endpoint comparison to:", file.path(dir_out_ol, "endpoints_comparison_hmc_vs_advi.csv"), "\n")

cat("\nTop 10 endpoints with largest median differences:\n")
if ("item_label_short" %in% names(endpoints_comparison)) {
    print(endpoints_comparison[1:10, .(item_label_short, variable, median_hmc, median_advi, median_diff)])
} else {
    print(endpoints_comparison[1:10, .(item_label, variable, median_hmc, median_advi, median_diff)])
}

# Create barplot with facet_wrap
# Combine HMC and ADVI for plotting
endpoints_combined <- rbind(endpoints_hmc, endpoints_advi)

# Filter for key variables of interest
endpoints_plot <- endpoints_combined[variable %in% c("diff", "ratio")]

# Create item identifier
if ("item_label_short" %in% names(endpoints_plot)) {
    endpoints_plot[, item_id := item_label_short]
} else {
    endpoints_plot[, item_id := item_label]
}

# Set method factor for consistent ordering
endpoints_plot[, method := factor(method, levels = c("HMC", "ADVI"))]

# Create y-axis labels based on item_type and variable
endpoints_plot[item_type == "out-of-7" & variable == "diff", 
               y_label := "Difference in mean days per week\n(Baseline - Endline)"]
endpoints_plot[item_type != "out-of-7" & variable == "diff", 
               y_label := "Difference in frequency\nof categories 'most of the time' and 'all of the time'"]
endpoints_plot[item_type == "out-of-7" & variable == "ratio", 
               y_label := "% change in mean days per week\n(1 - Endline/Baseline)"]
endpoints_plot[item_type != "out-of-7" & variable == "ratio", 
               y_label := "% change in frequency\nof categories 'most of the time' and 'all of the time'\n(1 - Endline/Baseline)"]

# Create facet label combining group and y-axis description
endpoints_plot[, facet_label := paste0(group_label_long, "\n", y_label)]

# Create separate plots for diff and ratio
# Plot 1: Difference (Baseline - Endline)
p_diff <- ggplot(
    endpoints_plot[variable == "diff"],
    aes(x = item_id, y = median, fill = method)
) +
    geom_col(position = position_dodge(width = 0.9), alpha = 0.8, width = 0.8) +
    geom_errorbar(
        aes(ymin = iqr_lower, ymax = iqr_upper),
        position = position_dodge(width = 0.9),
        width = 0.3,
        linewidth = 0.4
    ) +
    facet_wrap(~ facet_label, scales = "free", ncol = 2) +
    scale_fill_manual(values = c("HMC" = "#008080", "ADVI" = "#CA562C")) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 9),
        axis.text.y = element_text(size = 9),
        legend.position = "bottom",
        legend.title = element_text(size = 10, face = "bold"),
        legend.text = element_text(size = 9),
        strip.text = element_text(size = 9, face = "bold", lineheight = 1.1),
        strip.background = element_rect(fill = "transparent", color = NA),
        panel.spacing = unit(1, "lines"),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
        plot.margin = margin(10, 10, 10, 10)
    ) +
    labs(
        x = "Item", 
        y = "Estimate", 
        fill = "Method",
        title = "Endpoint Comparison: Difference"
    )

# Plot 2: Ratio (1 - Endline/Baseline)
p_ratio <- ggplot(
    endpoints_plot[variable == "ratio"],
    aes(x = item_id, y = median, fill = method)
) +
    geom_col(position = position_dodge(width = 0.9), alpha = 0.8, width = 0.8) +
    geom_errorbar(
        aes(ymin = iqr_lower, ymax = iqr_upper),
        position = position_dodge(width = 0.9),
        width = 0.3,
        linewidth = 0.4
    ) +
    facet_wrap(~ facet_label, scales = "free_y", ncol = 1) +
    scale_fill_manual(values = c("HMC" = "#008080", "ADVI" = "#CA562C")) +
    theme_minimal() +
    theme(
        axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 9),
        axis.text.y = element_text(size = 9),
        legend.position = "bottom",
        legend.title = element_text(size = 10, face = "bold"),
        legend.text = element_text(size = 9),
        strip.text = element_text(size = 9, face = "bold", lineheight = 1.1),
        strip.background = element_rect(fill = "transparent", color = NA),
        panel.spacing = unit(1, "lines"),
        plot.title = element_text(size = 12, face = "bold", hjust = 0.5),
        plot.margin = margin(10, 10, 10, 10)
    ) +
    labs(
        x = "Item", 
        y = "Estimate", 
        fill = "Method",
        title = "Endpoint Comparison: Ratio"
    )

# Save plots
ggsave(
    filename = file.path(dir_out_ol, "endpoints_comparison_barplot_diff.pdf"),
    plot = p_diff,
    h = 14,
    w = 12,
    limitsize = FALSE
)
ggsave(
    filename = file.path(dir_out_ol, "endpoints_comparison_barplot_diff.png"),
    plot = p_diff,
    h = 14,
    w = 12,
    limitsize = FALSE,
    dpi = 300
)

ggsave(
    filename = file.path(dir_out_ol, "endpoints_comparison_barplot_ratio.pdf"),
    plot = p_ratio,
    h = 14,
    w = 12,
    limitsize = FALSE
)
ggsave(
    filename = file.path(dir_out_ol, "endpoints_comparison_barplot_ratio.png"),
    plot = p_ratio,
    h = 14,
    w = 12,
    limitsize = FALSE,
    dpi = 300
)

cat("\nSaved endpoint comparison barplots (diff and ratio)\n")
```

## Compare ordered response probabilities for each survey item

```{r compare-ordered-probs, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Extract ordered_prob_by_cat_qu_fit parameters
prob_params <- grep("^ordered_prob_by_cat_qu_fit\\[", names(df_hmc), value = TRUE)
cat("Found", length(prob_params), "ordered_prob_by_cat_qu_fit parameters\n")

# Compute quantiles for each parameter under both methods
compute_quantiles <- function(df, params) {
    result <- data.table(parameter = params)
    result[, median := sapply(params, function(p) median(df[[p]]))]
    result[, q_05 := sapply(params, function(p) quantile(df[[p]], 0.05))]
    result[, q_25 := sapply(params, function(p) quantile(df[[p]], 0.25))]
    result[, q_75 := sapply(params, function(p) quantile(df[[p]], 0.75))]
    result[, q_975 := sapply(params, function(p) quantile(df[[p]], 0.975))]
    return(result)
}

probs_hmc <- compute_quantiles(df_hmc, prob_params)
setnames(probs_hmc, c("median", "q_05", "q_25", "q_75", "q_975"),
         c("median_hmc", "q_05_hmc", "q_25_hmc", "q_75_hmc", "q_975_hmc"))

probs_advi <- compute_quantiles(df_advi, prob_params)
setnames(probs_advi, c("median", "q_05", "q_25", "q_75", "q_975"),
         c("median_advi", "q_05_advi", "q_25_advi", "q_75_advi", "q_975_advi"))

# Merge and compute differences
probs_combined <- merge(probs_hmc, probs_advi, by = "parameter")
probs_combined[, median_diff := median_hmc - median_advi]
probs_combined[, abs_median_diff := abs(median_diff)]

# Order by absolute difference
setorder(probs_combined, -abs_median_diff)

cat("\nTop 10 ordered_prob_by_cat_qu_fit with largest median differences:\n")
print(probs_combined[1:10, .(parameter, median_hmc, median_advi, median_diff)])

# Save full results to CSV
fwrite(
    probs_combined,
    file = file.path(dir_out_ol, "ordered_prob_comparison_hmc_vs_advi.csv")
)
cat("\nSaved ordered_prob comparison to:", file.path(dir_out_ol, "ordered_prob_comparison_hmc_vs_advi.csv"), "\n")

# make plot

# Load data to get item mappings and empirical probabilities
tmp <- readRDS(paste0(output_file_prefix_hmc, "_data.rds"))
dp1 <- copy(tmp$dp1)
dit <- copy(tmp$dit)

# Load HMC draws in array format
poa <- readRDS(paste0(output_file_prefix_hmc, "_draws.rds"))

# Extract ordered_prob parameters from HMC
po_hmc <- poa[,, grepl("ordered_prob_by_cat_qu_fit", dimnames(poa)[[3]]), drop = FALSE]
po_hmc <- posterior::as_draws_df(po_hmc)
po_hmc <- as.data.table(po_hmc)
po_hmc <- data.table::melt(po_hmc,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po_hmc[, cq_id := as.integer(gsub(
    "ordered_prob_by_cat_qu_fit\\[([0-9]+)\\]", "\\1",
    variable
))]
set(po_hmc, NULL, "variable", NULL)

# Compute quantiles for HMC
pos_hmc <- po_hmc[,
    list(
        summary_value = quantile(prob, prob = c(0.25, 0.5, 0.75)),
        summary_name = c("q25", "median", "q75")
    ),
    by = c("cq_id")
]
pos_hmc <- data.table::dcast(pos_hmc,
    cq_id ~ summary_name,
    value.var = "summary_value"
)
pos_hmc[, method := "HMC"]

# Extract ordered_prob parameters from ADVI
poa_advi <- readRDS(paste0(output_file_prefix_advi, "_draws.rds"))
po_advi <- poa_advi[,, grepl("ordered_prob_by_cat_qu_fit", dimnames(poa_advi)[[3]]), drop = FALSE]
po_advi <- posterior::as_draws_df(po_advi)
po_advi <- as.data.table(po_advi)
po_advi <- data.table::melt(po_advi,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
)
po_advi[, cq_id := as.integer(gsub(
    "ordered_prob_by_cat_qu_fit\\[([0-9]+)\\]", "\\1",
    variable
))]
set(po_advi, NULL, "variable", NULL)

# Compute quantiles for ADVI
pos_advi <- po_advi[,
    list(
        summary_value = quantile(prob, prob = c(0.25, 0.5, 0.75)),
        summary_name = c("q25", "median", "q75")
    ),
    by = c("cq_id")
]
pos_advi <- data.table::dcast(pos_advi,
    cq_id ~ summary_name,
    value.var = "summary_value"
)
pos_advi[, method := "ADVI"]

# Combine HMC and ADVI
pos <- rbind(pos_hmc, pos_advi)

# Map cq_id back to (item_type_id, item_time_id, y_stan)
tmp_map <- unique(subset(dp1, select = c(item_type_id, item_label, item_time_id)))
tmp_map <- merge(tmp_map, subset(dit, select = c(item_type_id, item_label, cat_length)), by = c("item_type_id", "item_label"))
setkey(tmp_map, item_type_id, item_time_id)
tmp_map[, cq_id := cumsum(cat_length) - cat_length + 1L]
tmp_map <- tmp_map[, list(cq_id = cq_id - 1L + 1:cat_length, y = 1:cat_length - 1L), by = c("item_type_id", "item_time_id")]
tmp_map <- merge(tmp_map, 
                 unique(subset(dp1, 
                                select = c("item_type_id", "item_time_id", "y", "y_label", "item_label", "time_label")
                                )), 
                 by = c("item_type_id", "item_time_id", "y")
                 )
pos <- merge(tmp_map, pos, by = "cq_id")

# Compute empirical probabilities
tmp_emp <- dp1[,
    list(n = .N),
    by = c("time_label", "item_label", "y_label", "item_type_id", "item_time_id", "y")
]
tmp2 <- tmp_emp[, list(total = sum(n)), by = c("time_label", "item_label", "item_type_id", "item_time_id")]
tmp_emp <- merge(tmp_emp, tmp2, by = c("time_label", "item_label", "item_type_id", "item_time_id"))
tmp_emp[, median := n / total]
tmp_emp[, q25 := NA_real_]
tmp_emp[, q75 := NA_real_]
tmp_emp[, method := "Empirical"]
tmp_emp[, c("n", "total") := NULL]

# Merge with dit for plotting
pos <- merge(pos, dit, by = c("item_type_id","item_label"))
pos[, item_label_long := paste0(group_label_long, " --- ", item_label_short)]

# Add empirical data - merge with dit to get item_label_long
tmp_emp <- merge(tmp_emp, dit, by = c("item_type_id","item_label"))
tmp_emp[, item_label_long := paste0(group_label_long, " --- ", item_label_short)]

# Ensure tmp_emp has all columns that pos has (use common subset)
common_cols <- intersect(names(pos), names(tmp_emp))

# Combine HMC/ADVI with Empirical using rbind
pos <- rbind(
    pos[, ..common_cols],
    tmp_emp[, ..common_cols]
)

# Create plots: one subplot per item_label_long × time_label
items <- unique(pos$item_label_long)
times <- unique(pos$time_label)

plot_list <- list()
for (item in items) {
    for (t in times) {
        plot_data <- pos[item_label_long == item & time_label == t]
        
        # Set method factor levels for consistent ordering and colors
        plot_data[, method := factor(method, levels = c("Empirical", "HMC", "ADVI"))]
        
        p_sub <- ggplot(
            plot_data,
            aes(x = y_label, y = median, fill = method, group = interaction(method, y_label))
        ) +
            geom_col(position = position_dodge(width = 0.9), alpha = 0.7, width = 0.8) +
            geom_errorbar(
                aes(ymin = q25, ymax = q75),
                position = position_dodge(width = 0.9),
                width = 0.25
            ) +
            scale_y_continuous(labels = scales::percent, limits = c(0, NA)) +
            scale_fill_manual(values = c("Empirical" = "#B4C8A8", "HMC" = "#008080", "ADVI" = "#CA562C")) +
            ggtitle(paste0(item, " - ", t)) +
            theme_bw() +
            theme(
                axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 7),
                legend.position = "none",
                plot.title = element_text(size = 8)
            ) +
            labs(x = "", y = "probability", fill = "Method")
        
        plot_list[[paste(item, t, sep = "___")]] <- p_sub
    }
}

# Extract legend from one plot
p_legend <- ggplot(
    pos,
    aes(x = y_label, y = median, fill = method)
) +
    geom_col() +
    scale_fill_manual(
        values = c("Empirical" = "#B4C8A8", "HMC" = "#008080", "ADVI" = "#CA562C"),
        limits = c("Empirical", "HMC", "ADVI")
    ) +
    theme_bw() +
    theme(legend.position = "top") +
    labs(fill = "Method") +
    guides(fill = guide_legend(ncol = 3))

legend <- cowplot::get_legend(p_legend)

# Arrange plots in grid: 2 columns (Baseline and Endline for each item)
n_items <- length(items)
p <- cowplot::plot_grid(
    plotlist = plot_list,
    ncol = 2,
    align = "hv",
    axis = "tb"
)

# Add legend on top
p <- cowplot::plot_grid(legend, p, ncol = 1, rel_heights = c(0.05, 1))

ggsave(
    filename = file.path(dir_out_ol, "ordered_prob_comparison_by_item.pdf"),
    plot = p,
    h = 4 * n_items,
    w = 12,
    limitsize = FALSE
)
ggsave(
    filename = file.path(dir_out_ol, "ordered_prob_comparison_by_item.png"),
    plot = p,
    h = 4 * n_items,
    w = 12,
    limitsize = FALSE
)

cat("\nSaved item-level probability comparison plots\n")
```

## Compare core model parameters 

```{r compare-model-params, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Extract model parameter groups
param_groups <- list(
    latent_factor_unit = grep("^latent_factor_unit\\[", names(df_hmc), value = TRUE),
    skill_thresholds_1 = grep("^skill_thresholds_1\\[", names(df_hmc), value = TRUE),
    skill_thresholds_incs = grep("^skill_thresholds_incs\\[", names(df_hmc), value = TRUE),
    loadings_questions_m1 = grep("^loadings_questions_m1\\[", names(df_hmc), value = TRUE)
)

cat("Parameter counts:\n")
for (group in names(param_groups)) {
    cat("  ", group, ":", length(param_groups[[group]]), "\n")
}

# Compute quantiles for all model parameters
model_params_hmc <- compute_quantiles(df_hmc, unlist(param_groups))
setnames(model_params_hmc, c("median", "q_05", "q_25", "q_75", "q_975"),
         c("median_hmc", "q_05_hmc", "q_25_hmc", "q_75_hmc", "q_975_hmc"))

model_params_advi <- compute_quantiles(df_advi, unlist(param_groups))
setnames(model_params_advi, c("median", "q_05", "q_25", "q_75", "q_975"),
         c("median_advi", "q_05_advi", "q_25_advi", "q_75_advi", "q_975_advi"))

# Merge and compute differences
model_params_combined <- merge(model_params_hmc, model_params_advi, by = "parameter")
model_params_combined[, median_diff := median_hmc - median_advi]
model_params_combined[, abs_median_diff := abs(median_diff)]

# Add parameter group
model_params_combined[, param_group := NA_character_]
for (group in names(param_groups)) {
    model_params_combined[parameter %in% param_groups[[group]], param_group := group]
}

# Order by absolute difference within each group
setorder(model_params_combined, param_group, -abs_median_diff)

cat("\nTop 5 parameters per group with largest median differences:\n")
for (group in names(param_groups)) {
    cat("\n", group, ":\n")
    print(model_params_combined[param_group == group][1:min(5, .N), 
          .(parameter, median_hmc, median_advi, median_diff)])
}

# Save full results to CSV
fwrite(
    model_params_combined,
    file = file.path(dir_out_ol, "model_params_comparison_hmc_vs_advi.csv")
)
cat("\nSaved model params comparison to:", file.path(dir_out_ol, "model_params_comparison_hmc_vs_advi.csv"), "\n")

# make density plot
# Select top parameters from each group
top_per_group <- 8

top_model_params <- rbindlist(lapply(names(param_groups), function(group) {
    model_params_combined[param_group == group][1:min(top_per_group, .N), .(parameter, param_group)]
}))

# Prepare data for plotting (long format)
plot_data_model <- rbind(
    data.table::melt(
        as.data.table(df_hmc)[, c(".draw", top_model_params$parameter), with = FALSE],
        id.vars = ".draw",
        variable.name = "parameter",
        value.name = "value"
    )[, method := "HMC"],
    data.table::melt(
        as.data.table(df_advi)[, c(".draw", top_model_params$parameter), with = FALSE],
        id.vars = ".draw",
        variable.name = "parameter",
        value.name = "value"
    )[, method := "ADVI"]
)

# Add parameter group
plot_data_model <- merge(plot_data_model, top_model_params, by = "parameter")

# Create density plot faceted by parameter
p2 <- ggplot(plot_data_model, aes(x = value, color = method)) +
    geom_density(linewidth = 1.0, alpha = 0.8) +
    facet_wrap(~ parameter, scales = "free", ncol = 4) +
    scale_color_manual(values = c("HMC" = "#008080", "ADVI" = "#CA562C")) +
    theme_bw() +
    theme(
        legend.position = "top",
        strip.text = element_text(size = 7),
        axis.text = element_text(size = 6),
        axis.title = element_text(size = 9)
    ) +
    labs(
        title = "Comparison of Posterior Densities: Model Parameters",
        subtitle = paste("Top", top_per_group, "parameters per group ordered by largest difference"),
        x = "Parameter value",
        y = "Density",
        color = "Method"
    )

print(p2)

ggsave(
    filename = file.path(dir_out_ol, "model_params_comparison_densities.pdf"),
    plot = p2,
    width = 16,
    height = 12,
    dpi = 300
)

ggsave(
    filename = file.path(dir_out_ol, "model_params_comparison_densities.png"),
    plot = p2,
    width = 16,
    height = 12,
    dpi = 300
)
```

## Compare worst posterior predictions of outcomes

```{r compare-ypred, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Extract ypred parameters
ypred_params <- grep("^ypred\\[", names(df_hmc), value = TRUE)
cat("Found", length(ypred_params), "ypred parameters\n")

# Compute quantiles for ypred (including 25% and 75% for error bars)
compute_ypred_quantiles <- function(df, params) {
    result <- data.table(parameter = params)
    result[, median := sapply(params, function(p) median(df[[p]]))]
    result[, mean := sapply(params, function(p) mean(df[[p]]))]
    result[, q_25 := sapply(params, function(p) quantile(df[[p]], 0.25))]
    result[, q_75 := sapply(params, function(p) quantile(df[[p]], 0.75))]
    return(result)
}

ypred_hmc <- compute_ypred_quantiles(df_hmc, ypred_params)
setnames(ypred_hmc, c("median", "mean", "q_25", "q_75"),
         c("median_hmc", "mean_hmc", "q25_hmc", "q75_hmc"))

ypred_advi <- compute_ypred_quantiles(df_advi, ypred_params)
setnames(ypred_advi, c("median", "mean", "q_25", "q_75"),
         c("median_advi", "mean_advi", "q25_advi", "q75_advi"))

# Merge
ypred_combined <- merge(ypred_hmc, ypred_advi, by = "parameter")
ypred_combined[, median_diff := median_hmc - median_advi]
ypred_combined[, mean_diff := mean_hmc - mean_advi]
ypred_combined[, abs_median_diff := abs(median_diff)]

# Order by absolute median difference
setorder(ypred_combined, -abs_median_diff)

cat("\nTop 10 ypred with largest median differences:\n")
print(ypred_combined[1:10, .(parameter, median_hmc, median_advi, median_diff, mean_hmc, mean_advi)])

# Find parameters with disagreement (different medians rounded to nearest integer)
disagreements <- ypred_combined[round(median_hmc) != round(median_advi)]
cat("\nNumber of ypred parameters with different rounded medians:", nrow(disagreements), "out of", nrow(ypred_combined), "\n")
cat("Disagreement rate:", round(100 * nrow(disagreements) / nrow(ypred_combined), 2), "%\n")

# make plot
# Select top 30 by absolute median difference
top_n_ypred <- 30
top_ypred_params <- ypred_combined$parameter[1:top_n_ypred]

# Prepare data for plotting (using means for continuous comparison)
plot_data_ypred <- rbind(
    data.table(
        parameter = top_ypred_params,
        method = "HMC",
        mean = ypred_combined[1:top_n_ypred, mean_hmc],
        q25 = ypred_combined[1:top_n_ypred, q25_hmc],
        q75 = ypred_combined[1:top_n_ypred, q75_hmc]
    ),
    data.table(
        parameter = top_ypred_params,
        method = "ADVI",
        mean = ypred_combined[1:top_n_ypred, mean_advi],
        q25 = ypred_combined[1:top_n_ypred, q25_advi],
        q75 = ypred_combined[1:top_n_ypred, q75_advi]
    )
)

# Set factor levels to maintain order
plot_data_ypred[, parameter := factor(parameter, levels = rev(top_ypred_params))]

# Create bar plot with error bars
p3 <- ggplot(plot_data_ypred, aes(x = parameter, y = mean, fill = method)) +
    geom_col(position = position_dodge(width = 0.9), alpha = 0.7, width = 0.8) +
    geom_errorbar(
        aes(ymin = q25, ymax = q75),
        position = position_dodge(width = 0.9),
        width = 0.3
    ) +
    scale_fill_manual(values = c("HMC" = "#008080", "ADVI" = "#CA562C")) +
    coord_flip() +
    theme_bw() +
    theme(
        legend.position = "top",
        axis.text.y = element_text(size = 6),
        axis.text.x = element_text(size = 8),
        axis.title = element_text(size = 10)
    ) +
    labs(
        title = "Comparison of Posterior Means: ypred",
        subtitle = paste("Top", top_n_ypred, "parameters ordered by largest median difference\nError bars show 25%-75% quantiles"),
        x = "Parameter",
        y = "Posterior Mean",
        fill = "Method"
    )

print(p3)

ggsave(
    filename = file.path(dir_out_ol, "ypred_comparison_geom_col.pdf"),
    plot = p3,
    width = 14,
    height = 10,
    dpi = 300
)

ggsave(
    filename = file.path(dir_out_ol, "ypred_comparison_geom_col.png"),
    plot = p3,
    width = 14,
    height = 10,
    dpi = 300
)
```

## Summary of all comparisons

```{r final-summary, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
cat("\n=== SUMMARY OF HMC VS ADVI COMPARISON ===\n\n")

cat("1. ordered_prob_by_cat_qu_fit:\n")
cat("   - Total parameters:", nrow(probs_combined), "\n")
cat("   - Max absolute median difference:", round(max(probs_combined$abs_median_diff), 6), "\n")
cat("   - Mean absolute median difference:", round(mean(probs_combined$abs_median_diff), 6), "\n")
cat("   - Results saved to: ordered_prob_comparison_hmc_vs_advi.csv\n")
cat("   - Item-level plots: ordered_prob_comparison_by_item.{pdf,png}\n\n")

cat("2. Model parameters:\n")
for (group in names(param_groups)) {
    group_data <- model_params_combined[param_group == group]
    cat("   ", group, ":\n")
    cat("     - Parameters:", nrow(group_data), "\n")
    cat("     - Max abs diff:", round(max(group_data$abs_median_diff), 6), "\n")
    cat("     - Mean abs diff:", round(mean(group_data$abs_median_diff), 6), "\n")
}
cat("   - Results saved to: model_params_comparison_hmc_vs_advi.csv\n\n")

cat("3. ypred:\n")
cat("   - Total parameters:", nrow(ypred_combined), "\n")
cat("   - Disagreements (different rounded medians):", nrow(disagreements), "\n")
cat("   - Disagreement rate:", round(100 * nrow(disagreements) / nrow(ypred_combined), 2), "%\n")
cat("   - Max absolute median difference:", round(max(abs(ypred_combined$median_diff)), 4), "\n")
cat("   - Plots include 25%-75% quantile error bars\n\n")

cat("All plots and CSV files saved to:", dir_out_ol, "\n")
```