---
title: "Colombia plots and tables for the Hope Groups paper - partial credit model v251224"
date: "2025-12-30"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

We found the PCM model (v251224) performed best on the Colombia data among the three IRT models considered (ordered logistic model, credit model, partial credit model). This vignette generates plots and tables for the Hope Groups paper using the partial credit model v251224.

# Standalone model fit

## Load/Install packages

```{r load-packages, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Install and load packages
packages <- c(
    "cowplot",
    "data.table",
    "here",
    "purrr",
    "formatR",
    "ggplot2",
    "ggsci",
    "ggpubr",
    "hexbin",
    "bayesplot",
    "knitr",
    "kableExtra",
    "cmdstanr",
    "loo",
    "polycor",
    "GGally",
    "MatchIt"
)

# install.packages("remotes")  # if you don’t already have it
# remotes::install_github("stan-dev/cmdstanr") # if you don’t already have it

invisible(lapply(packages, function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg)
    library(pkg, character.only = TRUE)
  }
}))

```

```{r source-functions, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
source(here::here("R", "read_data_colombia.R"))
source(here::here("R", "read_data_ukraine.R"))
source(here::here("R", "train_test_split_data.R"))
source(here::here("R", "fit_credit_model.R"))
source(here::here("R", "fit_ordered_logit_model.R"))
source(here::here("R", "fit_partial_credit_model.R"))
source(here::here("R", "fit_partial_credit_model_ncats.R"))
```

## Run partial credit model v260413 on Colombia data (vanilla)

```{r define-data-locations-260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define directories
if (grepl("^/rds/general/user/or105", here::here())) {
    # Working on HPC
    on_hpc <- TRUE
    dir_data <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups/data"
    dir_out_base <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups"
} else {
    # Working locally
    on_hpc <- FALSE
    dir_data <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/data"
    dir_out_base <- "/Users/or105/sandbox"
}

# Define file names
file_data <- file.path(dir_data, "Colombia_data_baseline_endline_itemised_250927.csv")
file_data_quasi <- file.path(dir_data, "Colombia_data_quasi_assignments_250927.csv")

set.seed(42L)
seed <- c(123L)
```

```{r load-and-preprocess-data-colombia-260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Read in data from Colombia
tmp <- read_data_colombia(file_data)
dp_col <- copy(tmp$dp)
dit_col <- copy(tmp$dit)
dmeta_col <- copy(tmp$dmeta)

# Preprocess data
dp1_col <- subset(dp_col, !grepl("agg", item_label))
dp1_col[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1_col$item_label)),
    time = unique(dp1_col$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1_col <- merge(dp1_col, tmp, by = c("item_label", "time"))
dp1_col <- merge(dp1_col, unique(subset(dit_col, select = c(item_type, item_type_id))), by = "item_type")
setkey(dp1_col, item_type_id, pid, time, item_label)
dp1_col[, oid := .I]
setkey(dp1_col, oid)
tmp <- dp1_col[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1_col <- merge(dp1_col, tmp, by = c("item_type", "oid"))

setkey(dp1_col, pid, time, item_label)
```

```{r setup-pcm-directories-v260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-vanilla")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix <- file.path(dir_out_pcm, "pcm_1")
```

```{r compile-stan-model-pcm-v260413-vanilla, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "partial_credit_model_ncats_v260413.stan")
pcm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r pcm-fit-colombia-data-vanilla-v260413-vanilla, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
fit_partial_credit_model_ncats(
            dit_col,
            dp1_col,
            output_file_prefix = paste0(output_file_prefix, "_fit_vanilla"),
            stan_file = here::here("src", "stan", "partial_credit_model_ncats_v260413.stan"),
            chains = 4L,
            parallel_chains = 4L,
            threads_per_chain = 1L,
            iter_warmup = 500L,
            iter_sampling = 1000L,
            seed = seed,
            x_formula = ~ time - 1,
            resume = TRUE,
            with_core_analyses = TRUE,
            with_additional_analyses = TRUE,
            show_messages = TRUE,
            show_exceptions = TRUE
        )
gc()
```

## Run partial credit model v260413 on Colombia data with propensity score and time since death as fixed effects

```{r setup-pcm-directories-v260413, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix <- file.path(dir_out_pcm, "pcm_1")
```

```{r update-using-prepost-propensity-scores-260413, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Read in data from Colombia
tmp <- read_data_colombia(file_data)
dp_col <- copy(tmp$dp)
dit_col <- copy(tmp$dit)
dmeta_col <- copy(tmp$dmeta)

#  create propensity score and time since death as fixed effects for pre-post model
dmeta_col[, time := fifelse(time_label == "Baseline", 0, 1)]

ps_vars <- c(
  "time",
  "age",
  "sex",
  "stressmeals",
  "household_adults",
  "household_children",
  "child_impairment",
  "outfhelp",
  "ngp",
  "services_FOOD",
  "services_HOUSING_SUBS",
  "services_COUNSELING",
  "services_CHILDCARE",
  "education",
  "income.per.person",
  "maritalstat"
)

# Keep only observations with no missing values in PS variables
tmp <- unique(dmeta_col, by = c("pid_label", "time_label"))
tmp <- tmp[complete.cases(tmp[, ..ps_vars])]

# Make propensity score
fit_propensity <- glm(
  time ~ age + sex + stressmeals + household_adults + household_children + 
    child_impairment + outfhelp + ngp + services_FOOD + services_HOUSING_SUBS + 
    services_COUNSELING + services_CHILDCARE + education + income.per.person + 
    maritalstat, 
  family = "binomial", 
  data = tmp
)
tmp[, ps_score := predict(fit_propensity, type="response", data=tmp) ]
tmp <- subset(tmp, select = c("pid_label", "time_label", "ps_score", "time_since_death"))

# Add propensity scores and time since death to dp1_col
dp1_col <- subset(dp_col, !grepl("agg", item_label))
dp1_col <- merge(dp1_col, tmp, by=  c("pid_label", "time_label"))
dp1_col[, time_since_death_scaled := scale(time_since_death)]
dp1_col[, ps_score_scaled := scale(ps_score)]

# Preprocess data
dp1_col[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1_col$item_label)),
    time = unique(dp1_col$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1_col <- merge(dp1_col, tmp, by = c("item_label", "time"))
dp1_col <- merge(dp1_col, unique(subset(dit_col, select = c(item_type, item_type_id))), by = "item_type")
setkey(dp1_col, item_type_id, pid, time, item_label)
dp1_col[, oid := .I]
setkey(dp1_col, oid)
tmp <- dp1_col[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1_col <- merge(dp1_col, tmp, by = c("item_type", "oid"))
setkey(dp1_col, pid, time, item_label)

saveRDS(list(dp1 = dp1_col, dit = dit_col), paste0(output_file_prefix, "_ps_tsd_data.rds"))
```

```{r pcm-fit-colombia-propensity-scores-v260413, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
fit_partial_credit_model_ncats(
        dit_col,
        dp1_col,
        output_file_prefix = paste0(output_file_prefix, "_fit_ps_tsd"),
        stan_file = here::here("src", "stan", "partial_credit_model_ncats_v260413.stan"),
        chains = 4L,
        parallel_chains = 4L,
        threads_per_chain = 1L,
        iter_warmup = 500L,
        iter_sampling = 1000L,
        seed = seed,
        x_formula = ~ time + time_since_death_scaled + ps_score_scaled - 1, 
        resume = TRUE,
        with_core_analyses = TRUE,
        with_additional_analyses = TRUE,
        show_messages = TRUE,
        show_exceptions = TRUE
    )
gc()
```

## Run partial credit model v260413 on Colombia data with matched participants

```{r setup-pcm-directories-v260413-matched, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-matched-ps-tsd")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix <- file.path(dir_out_pcm, "pcm_1")
```

```{r load-and-preprocess-and-match-data-colombia-v260413-matched, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Read in data from Colombia
tmp <- read_data_colombia(file_data)
dp_col <- copy(tmp$dp)
dit_col <- copy(tmp$dit)
dmeta_col <- copy(tmp$dmeta)
dmeta_col[, time := fifelse(time_label == "Baseline", 0, 1)]

# Matching of study participants for quasi-experimental evaluation
match_data <- unique(dp_col[, .(pid_label, time_label, pid, time, submission_date)])
tmp <- unique(dmeta_col[, .(
  pid_label,
  time_label,
  age,
  sex,
  stressmeals,
  household_adults,
  household_children,
  child_impairment,
  outfhelp,
  ngp,
  services_FOOD,
  services_HOUSING_SUBS,
  services_COUNSELING,
  services_CHILDCARE,
  education,
  income.per.person,
  maritalstat,
  time_since_death
)])
match_data <- merge(match_data, tmp, by = c("pid_label", "time_label"))
match_data <- unique(match_data, by = c("pid_label", "time_label"))

# Creating needed date variables
match_data <- subset(match_data, !is.na(submission_date))
tmp <- min(match_data$submission_date)
match_data[, ref := round(difftime(submission_date, tmp, units = "days"))]
match_data[, ref_week := round(difftime(submission_date, tmp, units = "weeks"))]

# Dropping all baselines earlier than two weeks before first endline - no chance for match
match_data <- subset(match_data, submission_date > as.Date("26/04/2024", format = "%d/%m/%Y"))

# Matching
dmatched_col <- MatchIt::match.data(MatchIt::matchit( time ~ ref_week, data = match_data, method = "exact", replacement = FALSE ), drop.unmatched = FALSE)
dmatched_col <- as.data.table(dmatched_col)
setnames(dmatched_col, "subclass", "mid")
set(dmatched_col, NULL, 'mid', dmatched_col[, as.integer(mid)])

# Manually match participants with subclass==NA who fit within 2 weeks of another subclass.
dmatched_col[, mid := fcase(
  ref_week == 10L, 2L,
  ref_week == 25L, 34L,
  ref_week == 29L, 10L,
  ref_week == 39L, 13L,
  ref_week == 31L, 35L,
  ref_week == 47L, 31L,
  ref_week == 54L, 36L,
  ref_week == 58L, 6L,
  default = mid
)]

# Drop unmatched
dmatched_col <- subset(dmatched_col, !is.na(mid))

#  create propensity score and time since death as fixed effects for pre-post model
ps_vars <- c(
  "time",
  "age",
  "sex",
  "stressmeals",
  "household_adults",
  "household_children",
  "child_impairment",
  "outfhelp",
  "ngp",
  "services_FOOD",
  "services_HOUSING_SUBS",
  "services_COUNSELING",
  "services_CHILDCARE",
  "education",
  "income.per.person",
  "maritalstat"
)

# Keep only observations with no missing values in PS variables
tmp <- dmatched_col[complete.cases(dmatched_col[, ..ps_vars])]

# Make propensity score
fit_propensity <- glm(
  time ~ age + sex + stressmeals + household_adults + household_children + 
    child_impairment + outfhelp + ngp + services_FOOD + services_HOUSING_SUBS + 
    services_COUNSELING + services_CHILDCARE + education + income.per.person + 
    maritalstat, 
  family = "binomial", 
  data = tmp
)
tmp[, ps_score := predict(fit_propensity, type="response", data=tmp) ]
tmp <- subset(tmp, select = c("pid_label", "time_label", "mid", "ps_score", "time_since_death"))

# Add matchgin IDs, propensity scores and time since death to dp1_col
dp1_col <- subset(dp_col, !grepl("agg", item_label))
dp1_col <- merge(dp1_col, tmp, by=  c("pid_label", "time_label"))
dp1_col[, time_since_death_scaled := scale(time_since_death)]
dp1_col[, ps_score_scaled := scale(ps_score)]

# Preprocess data
dp1_col[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1_col$item_label)),
    time = unique(dp1_col$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1_col <- merge(dp1_col, tmp, by = c("item_label", "time"))
dp1_col <- merge(dp1_col, unique(subset(dit_col, select = c(item_type, item_type_id))), by = "item_type")
setkey(dp1_col, item_type_id, pid, time, item_label)
dp1_col[, oid := .I]
setkey(dp1_col, oid)
tmp <- dp1_col[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1_col <- merge(dp1_col, tmp, by = c("item_type", "oid"))
setkey(dp1_col, pid, time, item_label)

saveRDS(list(dp1 = dp1_col, dit = dit_col), paste0(output_file_prefix, "_matched_ps_tsd_data.rds"))
```

```{r pcm-fit-on-data-v260413-matched, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
fit_partial_credit_model_ncats(
        dit_col,
        dp1_col,
        output_file_prefix = paste0(output_file_prefix, "_fit_matched_ps_tsd"),
        stan_file = here::here("src", "stan", "partial_credit_model_ncats_v260413.stan"),
        x_formula = ~ time + factor(mid) + time_since_death_scaled + ps_score_scaled - 1, 
        x_formula_ignore_regex = "mid",
        chains = 4L,
        parallel_chains = 4L,
        threads_per_chain = 1L,
        iter_warmup = 500L,
        iter_sampling = 1000L,
        seed = seed,
        with_core_analyses = TRUE,
        with_additional_analyses = TRUE,
        show_messages = TRUE,
        show_exceptions = TRUE
    )
gc()
```

## Run partial credit model v260413 on Ukraine data, vanilla

```{r setup-pcm-directories-v260413-ukraine, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
# Define partial credit model output directories
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ukraine-comparison")
dir_logs_pcm <- file.path(dir_out_pcm, "logs")

# Create output directories if they don't exist
if (!dir.exists(dir_out_pcm)) {
    dir.create(dir_out_pcm, recursive = TRUE)
}
if (!dir.exists(dir_logs_pcm)) {
    dir.create(dir_logs_pcm, recursive = TRUE)
}

output_file_prefix <- file.path(dir_out_pcm, "pcm_1_ukraine")
```


```{r load-and-preprocess-data-ukraine, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
file_data_Ukraine <- file.path(dir_data, "Ukraine_Hope_Groups_Baseline_Endline_Wide_Aug6.csv")

# Read in data from Ukraine
tmp <- read_data_ukraine(file_data_Ukraine)
dp_ukr <- copy(tmp$dp)
dit_ukr <- copy(tmp$dit)
dmeta_ukr <- copy(tmp$dmeta)

# Preprocess data
dp1_ukr <- subset(dp_ukr, !grepl("agg", item_label))
dp1_ukr[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1_ukr$item_label)),
    time = unique(dp1_ukr$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1_ukr <- merge(dp1_ukr, tmp, by = c("item_label", "time"))
dp1_ukr <- merge(dp1_ukr, unique(subset(dit_ukr, select = c(item_type, item_type_id))), by = "item_type")
setkey(dp1_ukr, item_type_id, pid, time, item_label)
dp1_ukr[, oid := .I]
setkey(dp1_ukr, oid)
tmp <- dp1_ukr[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1_ukr <- merge(dp1_ukr, tmp, by = c("item_type", "oid"))
setkey(dp1_ukr, pid, time, item_label)

saveRDS(list(dp1 = dp1_ukr, dit = dit_ukr), paste0(output_file_prefix, "_vanilla_data.rds"))
```

```{r compile-stan-model-pcm-v260413-ukraine, include=FALSE, eval=FALSE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
stan_file <- here::here("src", "stan", "partial_credit_model_ncats_v260413.stan")
pcm_compiled <- cmdstanr::cmdstan_model(
        stan_file,
        include_paths = dirname(stan_file),
        cpp_options = list(stan_threads = TRUE),
        force_recompile = TRUE
    )
```

```{r pcm-fit-on-training-data-v260413-ukraine, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE, tidy=TRUE}
fit_partial_credit_model_ncats(
        dit_ukr,
        dp1_ukr,
        output_file_prefix = paste0(output_file_prefix, "_fit_vanilla"),
        stan_file = here::here("src", "stan", "partial_credit_model_ncats_v260413.stan"),
        chains = 4L,
        parallel_chains = 4L,
        threads_per_chain = 1L,
        iter_warmup = 500L,
        iter_sampling = 1000L,
        seed = seed,
        x_formula = ~ time - 1,
        resume = TRUE,
        with_core_analyses = TRUE,
        with_additional_analyses = TRUE,
        show_messages = TRUE,
        show_exceptions = TRUE
    )
gc()
```

# Plots and Tables

## Create primary endpoints for each outcome comprising multiple response items

Aggregate most + all of the time and compute mean for out-of-7

```{r colombia-endpoints, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, cache=TRUE}
# read fitted pcm model for Colombia data
if(1) {
    dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
    tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_ps_tsd_data.rds"))
    dp1 <- copy(tmp$dp1)
    dit <- copy(tmp$dit)        
    output_file_prefix <- file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_")    
    poa <- readRDS(paste0(output_file_prefix, "draws.rds"))
    categorical_threshold <- 3
}

# read fitted pcm model for Colombia data, matched participants
if(0) {
    dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-matched-ps-tsd")
    tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_matched_ps_tsd_data.rds"))
    dp1 <- copy(tmp$dp1)
    dit <- copy(tmp$dit)    
    output_file_prefix <- file.path(dir_out_pcm, "pcm_1_fit_matched_ps_tsd_")
    poa <- readRDS(paste0(output_file_prefix, "draws.rds"))
    categorical_threshold <- 3
}

# read fitted pcm model for Ukraine data
if(0) {
    dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ukraine-comparison")
    tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_ukraine_vanilla_data.rds"))
    dp1 <- copy(tmp$dp1)
    dit <- copy(tmp$dit)            
    output_file_prefix <- file.path(dir_out_pcm, "pcm_1_ukraine_fit_vanilla_")
    poa <- readRDS(paste0(output_file_prefix, "draws.rds"))    
    categorical_threshold <- 2
}

# Aggregate categorical probabilities for most + all of the time
po <- poa[,, grepl("ordered_prob_by_cat_qu_pr", dimnames(poa)[[3]]), drop = FALSE]            
po <- posterior::as_draws_df(po)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
    )
po[, cq_id := as.integer(gsub(
    "ordered_prob_by_cat_qu_pr\\[([0-9]+)\\]", "\\1",
    variable
    ))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1, select = c(item_type_id, item_label, item_time_id)))
tmp <- merge(tmp, subset(dit, select = c(item_type_id, item_label, cat_length)), by = c("item_type_id", "item_label"))
setkey(tmp, item_type_id, item_time_id)
tmp[, cq_id := cumsum(cat_length) - cat_length + 1L]
tmp <- tmp[, list(cq_id = cq_id - 1L + 1:cat_length, y = 1:cat_length - 1L), by = c("item_type_id", "item_time_id")]
po <- merge(tmp, po, by = "cq_id")   

tmp <- unique(subset(dp1[item_type == "categorical", ],
    select = c(item_type_id, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("item_type_id", "item_time_id"))
po <- subset(po, y >= categorical_threshold)
po <- po[,
    list(y_stan = 45, prob = sum(prob)),
    by = c(".draw", "item_type_id", "item_time_id", "item_label", "item_type", "time_label")
]
po <- merge(po, subset(dit, select = c(item_type, item_label, group_label)), by = c("item_type", "item_label"))
po <- po[,
    list(prob = mean(prob)),
    by = c(".draw", "item_type", "time_label", "group_label")
]
po <- data.table::dcast(po,
    .draw + item_type + group_label ~ time_label,
    value.var = "prob"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po[, diff := Baseline - Endline]
po[, ratio := 1 - Endline / Baseline]
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- melt(po,
    id.vars = c(".draw", "item_type", "group_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "Baseline", "Endline")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "group_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + group_label + variable ~ summary_name,
    value.var = "summary_value"
)
tmp <- unique(subset(dit, select = c(item_type, group_label, group_label_long, item_high_label)))
pos <- merge(pos, tmp, by = c("item_type", "group_label"))
pos_cat1 <- copy(pos)
po <- NULL
gc()

# Compute mean for out-of-7 responses
po <- poa[,, grepl("ordered_prob_by_cat_qu_pr", dimnames(poa)[[3]]), drop = FALSE]            
po <- posterior::as_draws_df(po)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
    )
po[, cq_id := as.integer(gsub(
    "ordered_prob_by_cat_qu_pr\\[([0-9]+)\\]", "\\1",
    variable
    ))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1, select = c(item_type_id, item_label, item_time_id)))
tmp <- merge(tmp, subset(dit, select = c(item_type_id, item_label, cat_length)), by = c("item_type_id", "item_label"))
setkey(tmp, item_type_id, item_time_id)
tmp[, cq_id := cumsum(cat_length) - cat_length + 1L]
tmp <- tmp[, list(cq_id = cq_id - 1L + 1:cat_length, y = 1:cat_length - 1L), by = c("item_type_id", "item_time_id")]
po <- merge(tmp, po, by = "cq_id")  

tmp <- unique(subset(dp1[item_type == "out-of-7", ],
    select = c(item_type_id, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("item_type_id", "item_time_id"))
po <- po[,
    list(mean = sum(y * prob)),
    by = c(".draw", "item_label", "item_time_id", "item_type", "time_label")
]
po <- merge(po, subset(dit, select = c(item_type, item_label, group_label)), by = c("item_type", "item_label"))
po <- po[,
    list(mean = mean(mean)),
    by = c(".draw", "item_type", "time_label", "group_label")
]
po <- data.table::dcast(po,
    .draw + item_type + group_label ~ time_label,
    value.var = "mean"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po <- merge(po,
    unique(subset(dit, select = c(item_type, group_label, item_high_label))),
    by = c("item_type", "group_label")
)
po[, diff := NA_real_]
po[, ratio := NA_real_]
tmp <- po[, which(item_high_label == "lower_is_better")]
set(po, tmp, "diff", po[tmp, Baseline - Endline])
set(po, tmp, "ratio", po[tmp, 1 - Endline / Baseline])
tmp <- po[, which(item_high_label == "higher_is_better")]
set(po, tmp, "diff", po[tmp, Endline - Baseline])
set(po, tmp, "ratio", po[tmp, Endline / Baseline - 1])
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- melt(po,
    id.vars = c(".draw", "item_type", "group_label", "item_high_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "Baseline", "Endline")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "group_label", "item_high_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + group_label + item_high_label + variable ~ summary_name,
    value.var = "summary_value"
)
tmp <- unique(subset(dit, select = c(item_type, group_label, group_label_long, item_high_label)))
pos <- merge(pos, tmp, by = c("item_type", "group_label", "item_high_label"))
pos_cat2 <- copy(pos)
po <- NULL
gc()

pos <- rbind(pos_cat1, pos_cat2, fill = TRUE)

cat("\nwrite endpoints to file=", paste0(output_file_prefix, "primary_endpoints_grouped.rds"), "\n")
saveRDS(pos,
    file = paste0(output_file_prefix, "primary_endpoints_grouped.rds"))
```

## Create primary endpoints for each response item

Aggregate most + all of the time and compute mean for out-of-7

```{r colombia-endpoints-detailed, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, cache=TRUE}
# read fitted pcm model for Colombia data
if(0) {
    dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
    tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_ps_tsd_data.rds"))
    dp1 <- copy(tmp$dp1)
    dit <- copy(tmp$dit)        
    output_file_prefix <- file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_")    
    poa <- readRDS(paste0(output_file_prefix, "draws.rds"))
    categorical_threshold <- 3
}

# read fitted pcm model for Colombia data, matched participants
if(0) {
    dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-matched-ps-tsd")
    tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_matched_ps_tsd_data.rds"))
    dp1 <- copy(tmp$dp1)
    dit <- copy(tmp$dit)    
    output_file_prefix <- file.path(dir_out_pcm, "pcm_1_fit_matched_ps_tsd_")
    poa <- readRDS(paste0(output_file_prefix, "draws.rds"))
    categorical_threshold <- 3
}

# read fitted pcm model for Ukraine data
if(1) {
    dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ukraine-comparison")
    tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_ukraine_vanilla_data.rds"))
    dp1 <- copy(tmp$dp1)
    dit <- copy(tmp$dit)            
    output_file_prefix <- file.path(dir_out_pcm, "pcm_1_ukraine_fit_vanilla_")
    poa <- readRDS(paste0(output_file_prefix, "draws.rds"))    
    categorical_threshold <- 2
}

# Aggregate categorical probabilities for most + all of the time
po <- poa[,, grepl("ordered_prob_by_cat_qu_pr", dimnames(poa)[[3]]), drop = FALSE]            
po <- posterior::as_draws_df(po)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
    )
po[, cq_id := as.integer(gsub(
    "ordered_prob_by_cat_qu_pr\\[([0-9]+)\\]", "\\1",
    variable
    ))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1, select = c(item_type_id, item_label, item_time_id)))
tmp <- merge(tmp, subset(dit, select = c(item_type_id, item_label, cat_length)), by = c("item_type_id", "item_label"))
setkey(tmp, item_type_id, item_time_id)
tmp[, cq_id := cumsum(cat_length) - cat_length + 1L]
tmp <- tmp[, list(cq_id = cq_id - 1L + 1:cat_length, y = 1:cat_length - 1L), by = c("item_type_id", "item_time_id")]
po <- merge(tmp, po, by = "cq_id")   

tmp <- unique(subset(dp1[item_type == "categorical", ],
    select = c(item_type_id, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("item_type_id", "item_time_id"))
po <- subset(po, y >= categorical_threshold)
po <- po[,
    list(y_stan = 45, prob = sum(prob)),
    by = c(".draw", "item_type_id", "item_time_id", "item_label", "item_type", "time_label")
]
po <- data.table::dcast(po,
    .draw + item_type + item_label ~ time_label,
    value.var = "prob"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po[, diff := Baseline - Endline]
po[, ratio := 1 - Endline / Baseline]
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- melt(po,
    id.vars = c(".draw", "item_type", "item_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "Baseline", "Endline")
)
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "item_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + item_label + variable ~ summary_name,
    value.var = "summary_value"
)
tmp <- unique(subset(dit, select = c(item_type, item_label, item_label_short, group_label, group_label_long, item_high_label)))
pos <- merge(pos, tmp, by = c("item_type", "item_label"))
pos_cat1 <- copy(pos)
po <- NULL
gc()

# Compute mean for out-of-7 responses
po <- poa[,, grepl("ordered_prob_by_cat_qu_pr", dimnames(poa)[[3]]), drop = FALSE]            
po <- posterior::as_draws_df(po)
po <- as.data.table(po)
po <- data.table::melt(po,
    id.vars = c(".draw", ".chain", ".iteration"),
    value.name = "prob"
    )
po[, cq_id := as.integer(gsub(
    "ordered_prob_by_cat_qu_pr\\[([0-9]+)\\]", "\\1",
    variable
    ))]
set(po, NULL, "variable", NULL)
tmp <- unique(subset(dp1, select = c(item_type_id, item_label, item_time_id)))
tmp <- merge(tmp, subset(dit, select = c(item_type_id, item_label, cat_length)), by = c("item_type_id", "item_label"))
setkey(tmp, item_type_id, item_time_id)
tmp[, cq_id := cumsum(cat_length) - cat_length + 1L]
tmp <- tmp[, list(cq_id = cq_id - 1L + 1:cat_length, y = 1:cat_length - 1L), by = c("item_type_id", "item_time_id")]
po <- merge(tmp, po, by = "cq_id")  

tmp <- unique(subset(dp1[item_type == "out-of-7", ],
    select = c(item_type_id, item_label, item_time_id, item_type, time_label)
))
po <- merge(po, tmp, by = c("item_type_id", "item_time_id"))
po <- po[,
    list(mean = sum(y * prob)),
    by = c(".draw", "item_label", "item_time_id", "item_type", "time_label")
]
po <- data.table::dcast(po,
    .draw + item_type + item_label ~ time_label,
    value.var = "mean"
)
po <- subset(po, !is.na(Baseline) & !is.na(Endline))
po <- merge(po,
    unique(subset(dit, select = c(item_type, item_label, group_label, item_high_label))),
    by = c("item_type", "item_label")
)
po[, diff := NA_real_]
po[, ratio := NA_real_]
tmp <- po[, which(item_high_label == "lower_is_better")]
set(po, tmp, "diff", po[tmp, Baseline - Endline])
set(po, tmp, "ratio", po[tmp, 1 - Endline / Baseline])
tmp <- po[, which(item_high_label == "higher_is_better")]
set(po, tmp, "diff", po[tmp, Endline - Baseline])
set(po, tmp, "ratio", po[tmp, Endline / Baseline - 1])
po[, diff2 := Endline - Baseline]
po[, ratio2 := Endline / Baseline - 1]
po <- melt(po,
    id.vars = c(".draw", "item_type", "item_label", "item_high_label"),
    measure.vars = c("diff", "ratio", "diff2", "ratio2", "Baseline", "Endline")
    )
pos <- po[,
    list(
        summary_value = quantile(value, prob = c(0.025, 0.25, 0.5, 0.75, 0.975)),
        summary_name = c("q_lower", "iqr_lower", "median", "iqr_upper", "q_upper")
    ),
    by = c("item_type", "item_label", "item_high_label", "variable")
]
pos <- data.table::dcast(pos,
    item_type + item_label + item_high_label + variable ~ summary_name,
    value.var = "summary_value"
)
tmp <- unique(subset(dit, select = c(item_type, item_label, item_label_short, group_label, group_label_long, item_high_label)))
pos <- merge(pos, tmp, by = c("item_type", "item_label", "item_high_label"))
pos_cat2 <- copy(pos)
po <- NULL
gc()

pos <- rbind(pos_cat1, pos_cat2, fill = TRUE)

cat("\nwrite endpoints to file=", paste0(output_file_prefix, "primary_endpoints_detailed.rds"), "\n")
saveRDS(pos,
    file = paste0(output_file_prefix, "primary_endpoints_detailed.rds"))
```

## Table 2 of primary endpoints in Colombia, aggregated, both pre-post and quasi-experimental

```{r make-table-2, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_primary_endpoints_grouped.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
pos[, analysis := 'prepost']

dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-matched-ps-tsd")
tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_matched_ps_tsd_primary_endpoints_grouped.rds"))
tmp <- subset(tmp, variable %in% c('Baseline','Endline','ratio2','diff2'))
tmp[, analysis := 'quasiexp']
pos <- rbind(pos, tmp, fill = TRUE)
set(pos, NULL, "variable", pos[, gsub("Baseline", "bl", variable)])
set(pos, NULL, "variable", pos[, gsub("Endline", "el", variable)])

output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope \\\\and Resilience"]
pos[group_label_long == "Caregiver exercising nonviolent discipline", group_label_long := "Caregiver exercising \\\\ nonviolent discipline"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression \\\\ and Anxiety']

# Recode item_high_label for display
pos[, item_high_label := ifelse(item_high_label == "lower_is_better", "Lower", "Higher")]
pos[, item_high_label := factor(item_high_label, levels = c("Lower", "Higher"))]

# Format numbers
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp] * 100, 1))
}
tmp <- pos[, which(!(variable %in% c('ratio2') | item_type == 'categorical'))]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp], 1))
}
pos[, value_string := NA_character_]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    " \\\\ (",
    sprintf("%.1f", q_lower),
    ", ",
    sprintf("%.1f", q_upper),
    ")}"
)])
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    "\\% \\\\ (",
    sprintf("%.1f", q_lower),
    "\\%, ",
    sprintf("%.1f", q_upper),
    "\\%)}"
)])

# Recode item_type for display
pos[item_type == "categorical", item_type := "$^\\dagger$"]
pos[item_type == "out-of-7", item_type := "$^\\ddagger$"]

# Reshape for table
pos <- dcast.data.table(pos,
    analysis + item_type + group_label_long + item_high_label ~ variable,
    value.var = "value_string"
)

# Create outcome domain with superscript for footnote
pos[, outcome_domain := paste0('\\makecell{',group_label_long, item_type, "}")]
pos[, type := ""]

# Save as CSV (include original columns for reference)
fwrite(pos, file = paste0(output_file_prefix, "_supp_table_1.csv"))


pos1 <- subset(pos, 
    analysis == "prepost" & 
    !group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues")
    )
pos2 <- subset(pos, 
    analysis == "prepost" & 
    group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues")
    )
pos3 <- subset(pos, 
    analysis == "quasiexp" & 
    !group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues")
    )
pos4 <- subset(pos, 
    analysis == "quasiexp" & 
    group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues")
    )

# Reorder and select columns for display 
pos1 <- pos1[, c("type","outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2")]
pos2 <- pos2[, c("type","outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2")]
pos3 <- pos3[, c("type","outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2")]
pos4 <- pos4[, c("type","outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2")]

# Recode names for display
setnames(pos1,
    old = c("type", "outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)
setnames(pos2,
    old = c("type", "outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)
setnames(pos3,
    old = c("type", "outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)
setnames(pos4,
    old = c("type", "outcome_domain", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

# Create LaTeX table
latex_table1 <- kable(pos1, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table1 <- strsplit(latex_table1, "\n")[[1]]
latex_table2 <- kable(pos2, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table2 <- strsplit(latex_table2, "\n")[[1]]
latex_table3 <- kable(pos3, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table3 <- strsplit(latex_table3, "\n")[[1]]
latex_table4 <- kable(pos4, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table4 <- strsplit(latex_table4, "\n")[[1]]

# Create standalone LaTeX document with threeparttable for footnotes
latex_doc <- paste0(
    "\\documentclass{article}\n",
    "\\usepackage{booktabs}\n",
    "\\usepackage{longtable}\n",
    "\\usepackage{array}\n",
    "\\usepackage{multirow}\n",
    "\\usepackage{wrapfig}\n",
    "\\usepackage{float}\n",
    "\\usepackage{colortbl}\n",
    "\\usepackage{pdflscape}\n",
    "\\usepackage{tabu}\n",
    "\\usepackage{threeparttable}\n",
    "\\usepackage{threeparttablex}\n",
    "\\usepackage[normalem]{ulem}\n",
    "\\usepackage{makecell}\n",
    "\\usepackage{xcolor}\n",
    "\\usepackage[margin=1in]{geometry}\n",
    "\\usepackage{caption}\n",
    "\\setcounter{table}{1}\n",
    "\\captionsetup[table]{skip=10pt, font=bf}\n",
    "\\begin{document}\n",
    "\\thispagestyle{empty}\n",
    "\\begin{table}[H]\n",
    "\\centering\\renewcommand\\cellalign{lc}\n",
    "\\setcellgapes{3pt}\\makegapedcells\n",
    "\\centering\n",
    "\\caption{Changes in outcomes following Hope Group participation among next-of-kin caregivers in Colombia in 2024-2025, utilising pre-post and quasi-experimental methodologies}\n",
    "\\begin{threeparttable}\n",
    "\\resizebox*{!}{1.15\\textwidth}\n",
    "{\n",
    "\\small\n",
    "\\centering\n",
    paste0(latex_table1[1:5], collapse = "\n"),
    "\\textbf{Primary} & & & & & & \\\\ \n",
    "\\multicolumn{7}{l}{\\textbf{Pre-Post Findings}} \\\\ \n",
    paste0(latex_table1[6:12], collapse = "\n"),
    "\\multicolumn{7}{l}{\\textbf{Quasi-Experimental Findings}} \\\\ \n",
    paste0(latex_table3[6:12], collapse = "\n"),
    "\\midrule\\textbf{Secondary} & & & & & & \\\\ \n",
    "\\multicolumn{7}{l}{\\textbf{Pre-Post Findings}} \\\\ \n",
    paste0(latex_table2[6:8], collapse = "\n"),
    "\\multicolumn{7}{l}{\\textbf{Quasi-Experimental Findings}} \\\\ \n",
    paste0(latex_table4[6:9], collapse = "\n"),
    "\\multicolumn{7}{l}{$^\\dagger$ Unit of outcome: frequency of the two categories 'most of the time' and 'all of the time'.} \\\\ \n",    
    "\\multicolumn{7}{l}{$^\\ddagger$ Unit of outcome: mean days per week.} \\\\ \n",
    paste0(latex_table2[10], collapse = "\n"),
    "}\n", 
    "\\end{threeparttable}\n",
    "\\end{table}\n",
    "\\end{document}"
)

# Write LaTeX file
latex_file <- paste0(output_file_prefix, "_table_2.tex")
writeLines(latex_doc, latex_file)

# Compile to PDF
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))  # Run twice for proper formatting

cat("\nSupplementary Table 1 saved to:\n")
cat("  CSV: ", paste0(output_file_prefix, "_table_2.csv"), "\n")
cat("  LaTeX: ", latex_file, "\n")
cat("  PDF: ", paste0(output_file_prefix, "_table_2.pdf"), "\n")

```

## Supplementary Table 1 of primary endpoints in Colombia, by items, pre-post

```{r make-supp-table-1, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_primary_endpoints_detailed.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
set(pos, NULL, "variable", pos[, gsub("Baseline", "bl", variable)])
set(pos, NULL, "variable", pos[, gsub("Endline", "el", variable)])
pos <- subset(pos, variable %in% c('bl','el','ratio2','diff2'))

output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope \\\\and Resilience"]
pos[group_label_long == "Caregiver exercising nonviolent discipline", group_label_long := "Caregiver exercising \\\\ nonviolent discipline"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression \\\\ and Anxiety']

pos[, item_label_long := NA_character_]
tmp <- pos[, which(item_label_short == '')]
set(pos, tmp, 'item_label_long', pos[tmp, group_label_long])
tmp <- pos[, which(item_label_short != '')]
set(pos, tmp, 'item_label_long', pos[tmp, paste0(group_label_long, ": \\\\ ", item_label_short)])

# Recode item_high_label for display
pos[, item_high_label := ifelse(item_high_label == "lower_is_better", "Lower", "Higher")]
pos[, item_high_label := factor(item_high_label, levels = c("Lower", "Higher"))]

# Format numbers
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp] * 100, 1))
}
tmp <- pos[, which(!(variable %in% c('ratio2') | item_type == 'categorical'))]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp], 1))
}
pos[, value_string := NA_character_]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    " \\\\ (",
    sprintf("%.1f", q_lower),
    ", ",
    sprintf("%.1f", q_upper),
    ")}"
)])
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    "\\% \\\\ (",
    sprintf("%.1f", q_lower),
    "\\%, ",
    sprintf("%.1f", q_upper),
    "\\%)}"
)])

# Recode item_type for display
pos[item_type == "categorical", item_type := "$^\\dagger$"]
pos[item_type == "out-of-7", item_type := "$^\\ddagger$"]

# Reshape for table
pos <- dcast.data.table(pos,
    item_type + group_label_long + item_label_long + item_high_label ~ variable,
    value.var = "value_string"
)

# Create outcome domain with superscript for footnote
pos[, item_label_long := paste0('\\makecell{',item_label_long, item_type, "}")]
pos[, type := ""]

# Save as CSV (include original columns for reference)
fwrite(pos, file = paste0(output_file_prefix, "_supp_table_2.csv"))


pos1 <- subset(pos, !group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

pos2 <- subset(pos, group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

# Reorder and select columns for display 
pos1 <- pos1[, c("type","item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2")]
pos2 <- pos2[, c("type","item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2")]

# Recode names for display
setnames(pos1,
    old = c("type", "item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Item}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

setnames(pos2,
    old = c("type", "item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Item}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

# Create LaTeX table
latex_table1 <- kable(pos1, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table1 <- strsplit(latex_table1, "\n")[[1]]
latex_table2 <- kable(pos2, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table2 <- strsplit(latex_table2, "\n")[[1]]

# Create standalone LaTeX document with threeparttable for footnotes
latex_doc <- paste0(
    "\\documentclass{article}\n",
    "\\usepackage{booktabs}\n",
    "\\usepackage{longtable}\n",
    "\\usepackage{array}\n",
    "\\usepackage{multirow}\n",
    "\\usepackage{wrapfig}\n",
    "\\usepackage{float}\n",
    "\\usepackage{colortbl}\n",
    "\\usepackage{pdflscape}\n",
    "\\usepackage{tabu}\n",
    "\\usepackage{threeparttable}\n",
    "\\usepackage{threeparttablex}\n",
    "\\usepackage[normalem]{ulem}\n",
    "\\usepackage{makecell}\n",
    "\\usepackage{xcolor}\n",
    "\\usepackage[margin=1in]{geometry}\n",
    "\\renewcommand{\\thetable}{S\\arabic{table}}\n",
    "\\usepackage{caption}\n",
    "\\captionsetup[table]{skip=10pt, font=bf}\n",
    "\\begin{document}\n",
    "\\setcounter{table}{0}\n",
    "\\thispagestyle{empty}\n",
    "\\begin{table}[H]\n",
    "\\centering\\renewcommand\\cellalign{lc}\n",
    "\\setcellgapes{3pt}\\makegapedcells\n",
    "\\centering\n",
    "\\caption{Changes in response items following Parenting with Hope participation among next-of-kin caregivers in Colombia in 2024-2025, in the pre-post analysis}\n",
    "\\begin{threeparttable}\n",
    "\\resizebox*{!}{1.2\\textwidth}\n",
    "{\n",
    "\\small\n",
    "\\centering\n",
    paste0(latex_table1[1:5], collapse = "\n"),
    "\\multicolumn{7}{l}{\\textbf{Primary (pre-post analysis)}} \\\\ \n",
    paste0(latex_table1[6:21], collapse = "\n"),
    "\\midrule\\multicolumn{7}{l}{\\textbf{Secondary (pre-post analysis)}} \\\\ \n",
    paste0(latex_table2[6:11], collapse = "\n"), '\n',
    "\\multicolumn{7}{l}{$^\\dagger$ Unit of outcome: frequency of the two categories 'most of the time' and 'all of the time'.} \\\\ \n",    
    "\\multicolumn{7}{l}{$^\\ddagger$ Unit of outcome: mean days per week.} \\\\ \n",
    paste0(latex_table2[12], collapse = "\n"),
    "}\n", 
    "\\end{threeparttable}\n",
    "\\end{table}\n",
    "\\end{document}"
)

# Write LaTeX file
latex_file <- paste0(output_file_prefix, "_supp_table_1.tex")
writeLines(latex_doc, latex_file)

# Compile to PDF
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))  # Run twice for proper formatting

cat("\nSupplementary Table 1 saved to:\n")
cat("  CSV: ", paste0(output_file_prefix, "_supp_table_1.csv"), "\n")
cat("  LaTeX: ", latex_file, "\n")
cat("  PDF: ", paste0(output_file_prefix, "_supp_table_1.pdf"), "\n")
```

## Supplementary Table 2 of primary endpoints in Colombia, by items, quasi-experimental

```{r make-supp-table-1, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-matched-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_matched_ps_tsd_primary_endpoints_detailed.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
set(pos, NULL, "variable", pos[, gsub("Baseline", "bl", variable)])
set(pos, NULL, "variable", pos[, gsub("Endline", "el", variable)])

output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope \\\\and Resilience"]
pos[group_label_long == "Caregiver exercising nonviolent discipline", group_label_long := "Caregiver exercising \\\\ nonviolent discipline"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression \\\\ and Anxiety']

pos[, item_label_long := NA_character_]
tmp <- pos[, which(item_label_short == '')]
set(pos, tmp, 'item_label_long', pos[tmp, group_label_long])
tmp <- pos[, which(item_label_short != '')]
set(pos, tmp, 'item_label_long', pos[tmp, paste0(group_label_long, ": \\\\ ", item_label_short)])

# Recode item_high_label for display
pos[, item_high_label := ifelse(item_high_label == "lower_is_better", "Lower", "Higher")]
pos[, item_high_label := factor(item_high_label, levels = c("Lower", "Higher"))]

# Format numbers
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp] * 100, 1))
}
tmp <- pos[, which(!(variable %in% c('ratio2') | item_type == 'categorical'))]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp], 1))
}
pos[, value_string := NA_character_]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    " \\\\ (",
    sprintf("%.1f", q_lower),
    ", ",
    sprintf("%.1f", q_upper),
    ")}"
)])
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    "\\% \\\\ (",
    sprintf("%.1f", q_lower),
    "\\%, ",
    sprintf("%.1f", q_upper),
    "\\%)}"
)])

# Recode item_type for display
pos[item_type == "categorical", item_type := "$^\\dagger$"]
pos[item_type == "out-of-7", item_type := "$^\\ddagger$"]

# Reshape for table
pos <- dcast.data.table(pos,
    item_type + group_label_long + item_label_long + item_high_label ~ variable,
    value.var = "value_string"
)

# Create outcome domain with superscript for footnote
pos[, item_label_long := paste0('\\makecell{',item_label_long, item_type, "}")]
pos[, type := ""]

# Save as CSV (include original columns for reference)
fwrite(pos, file = paste0(output_file_prefix, "_supp_table_2.csv"))


pos1 <- subset(pos, !group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

pos2 <- subset(pos, group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

# Reorder and select columns for display 
pos1 <- pos1[, c("type","item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2")]
pos2 <- pos2[, c("type","item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2")]

# Recode names for display
setnames(pos1,
    old = c("type", "item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Item}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

setnames(pos2,
    old = c("type", "item_label_long", "item_high_label", "bl", "el", "diff2", "ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Item}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

# Create LaTeX table
latex_table1 <- kable(pos1, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table1 <- strsplit(latex_table1, "\n")[[1]]
latex_table2 <- kable(pos2, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l","l","l","l","l")
)
latex_table2 <- strsplit(latex_table2, "\n")[[1]]

# Create standalone LaTeX document with threeparttable for footnotes
latex_doc <- paste0(
    "\\documentclass{article}\n",
    "\\usepackage{booktabs}\n",
    "\\usepackage{longtable}\n",
    "\\usepackage{array}\n",
    "\\usepackage{multirow}\n",
    "\\usepackage{wrapfig}\n",
    "\\usepackage{float}\n",
    "\\usepackage{colortbl}\n",
    "\\usepackage{pdflscape}\n",
    "\\usepackage{tabu}\n",
    "\\usepackage{threeparttable}\n",
    "\\usepackage{threeparttablex}\n",
    "\\usepackage[normalem]{ulem}\n",
    "\\usepackage{makecell}\n",
    "\\usepackage{xcolor}\n",
    "\\usepackage[margin=1in]{geometry}\n",
    "\\renewcommand{\\thetable}{S\\arabic{table}}\n",
    "\\usepackage{caption}\n",
    "\\captionsetup[table]{skip=10pt, font=bf}\n",
    "\\begin{document}\n",
    "\\setcounter{table}{1}\n",
    "\\thispagestyle{empty}\n",
    "\\begin{table}[H]\n",
    "\\centering\\renewcommand\\cellalign{lc}\n",
    "\\setcellgapes{3pt}\\makegapedcells\n",
    "\\centering\n",
    "\\caption{Changes in response items following Parenting with Hope participation among next-of-kin caregivers in Colombia in 2024-2025, in the quasi-experimental analysis}\n",
    "\\begin{threeparttable}\n",
    "\\resizebox*{!}{1.2\\textwidth}\n",
    "{\n",
    "\\small\n",
    "\\centering\n",
    paste0(latex_table1[1:5], collapse = "\n"),
    "\\multicolumn{7}{l}{\\textbf{Primary (quasi-experimental analysis)}} \\\\ \n",
    paste0(latex_table1[6:21], collapse = "\n"),
    "\\midrule\\multicolumn{7}{l}{\\textbf{Secondary (quasi-experimental analysis)}} \\\\ \n",
    paste0(latex_table2[6:11], collapse = "\n"), '\n',
    "\\multicolumn{7}{l}{$^\\dagger$ Unit of outcome: frequency of the two categories 'most of the time' and 'all of the time'.} \\\\ \n",    
    "\\multicolumn{7}{l}{$^\\ddagger$ Unit of outcome: mean days per week.} \\\\ \n",
    paste0(latex_table2[12], collapse = "\n"),
    "}\n", 
    "\\end{threeparttable}\n",
    "\\end{table}\n",
    "\\end{document}"
)

# Write LaTeX file
latex_file <- paste0(output_file_prefix, "_supp_table_2.tex")
writeLines(latex_doc, latex_file)

# Compile to PDF
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))  # Run twice for proper formatting

cat("\nSupplementary Table 2 saved to:\n")
cat("  CSV: ", paste0(output_file_prefix, "_supp_table_2.csv"), "\n")
cat("  LaTeX: ", latex_file, "\n")
cat("  PDF: ", paste0(output_file_prefix, "_supp_table_2.pdf"), "\n")
```

## Supplementary Table 3 comparing primary endpoints in Colombia to those in Ukraine

```{r make-supp-table-3, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_primary_endpoints_grouped.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
pos[, country := 'Colombia']

dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ukraine-comparison")
tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_ukraine_fit_vanilla_primary_endpoints_grouped.rds"))
tmp <- subset(tmp, variable %in% c('Baseline','Endline','ratio2','diff2'))
tmp[, country := 'Ukraine']
tmp <- subset(tmp, group_label_long != 'grieve')

pos <- rbind(pos, tmp, fill = TRUE)
set(pos, NULL, "variable", pos[, gsub("Baseline", "bl", variable)])
set(pos, NULL, "variable", pos[, gsub("Endline", "el", variable)])

output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope \\\\and Resilience"]
pos[group_label_long == "Caregiver exercising nonviolent discipline", group_label_long := "Caregiver exercising \\\\ nonviolent discipline"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression \\\\ and Anxiety']

# Recode item_high_label for display
pos[, item_high_label := ifelse(item_high_label == "lower_is_better", "Lower", "Higher")]
pos[, item_high_label := factor(item_high_label, levels = c("Lower", "Higher"))]

# Format numbers
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp] * 100, 1))
}
tmp <- pos[, which(!(variable %in% c('ratio2') | item_type == 'categorical'))]
for(x in c('iqr_lower','iqr_upper','median','q_lower','q_upper')){
    set(pos, tmp, x, round(pos[[x]][tmp], 1))
}
pos[, value_string := NA_character_]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    " \\\\ (",
    sprintf("%.1f", q_lower),
    ", ",
    sprintf("%.1f", q_upper),
    ")}"
)])
tmp <- pos[, which(variable %in% c('ratio2') | item_type == 'categorical')]
set(pos, tmp, 'value_string', pos[tmp, paste0("\\makecell{",
    sprintf("%.1f", median),
    "\\% \\\\ (",
    sprintf("%.1f", q_lower),
    "\\%, ",
    sprintf("%.1f", q_upper),
    "\\%)}"
)])

# Recode item_type for display
pos[item_type == "categorical", item_type := "$^\\dagger$"]
pos[item_type == "out-of-7", item_type := "$^\\ddagger$"]

# Reshape for table
pos <- dcast.data.table(pos,
    item_type + group_label_long + item_high_label ~ country + variable,
    value.var = "value_string"
)

# Create outcome domain with superscript for footnote
pos[, outcome_domain := paste0('\\makecell{',group_label_long, item_type, "}")]
pos[, type := ""]

# Save as CSV (include original columns for reference)
fwrite(pos, file = paste0(output_file_prefix, "_supp_table_3.csv"))


pos1 <- subset(pos, !group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

pos2 <- subset(pos, group_label_long %in% c("Caregiver Hope \\\\and Resilience", "Caregiver self-care", "Child behavioural issues"))

# Reorder and select columns for display 
pos1 <- pos1[, c("type","outcome_domain", "item_high_label", 
                 "Colombia_bl", "Colombia_el", "Colombia_diff2", "Colombia_ratio2", 
                 "Ukraine_bl", "Ukraine_el", "Ukraine_diff2", "Ukraine_ratio2")]
pos2 <- pos2[, c("type","outcome_domain", "item_high_label", 
                 "Colombia_bl", "Colombia_el", "Colombia_diff2", "Colombia_ratio2", 
                 "Ukraine_bl", "Ukraine_el", "Ukraine_diff2", "Ukraine_ratio2")]

# Recode names for display
setnames(pos1,
    old = c("type", "outcome_domain", "item_high_label", "Colombia_bl", "Colombia_el", "Colombia_diff2", "Colombia_ratio2", 
                 "Ukraine_bl", "Ukraine_el", "Ukraine_diff2", "Ukraine_ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}",
    "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

setnames(pos2,
    old = c("type", "outcome_domain", "item_high_label", "Colombia_bl", "Colombia_el", "Colombia_diff2", "Colombia_ratio2", 
                 "Ukraine_bl", "Ukraine_el", "Ukraine_diff2", "Ukraine_ratio2"),
    new = c("\\textbf{Type}", "\\textbf{Outcome}", "\\textbf{\\makecell{Direction \\\\ of Impro- \\\\ vement}}", "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}",
    "\\makecell{\\textbf{Baseline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Endline}\\\\ \\\\(median, 95\\% CrI)}", "\\makecell{\\textbf{Difference} \\\\ \\textbf{(Endline vs Baseline)} \\\\ (median, 95\\% CrI)}", "\\makecell{\\textbf{Percent change} \\\\ \\textbf{(Endline vs Baseline)} \\\\(median, 95\\% CrI)}")
)

# Create LaTeX table
latex_table1 <- kable(pos1, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l|","l","l","l","l|","l","l","l","l")
)
latex_table1 <- strsplit(latex_table1, "\n")[[1]]
latex_table2 <- kable(pos2, 
    format = "latex",
    booktabs = TRUE,
    longtable = FALSE,
    escape = FALSE,
    linesep = "",
    align = c("l","l","l|","l","l","l","l|","l","l","l","l")
)
latex_table2 <- strsplit(latex_table2, "\n")[[1]]

# Create standalone LaTeX document with threeparttable for footnotes
latex_doc <- paste0(
    "\\documentclass{article}\n",
    "\\usepackage{booktabs}\n",
    "\\usepackage{longtable}\n",
    "\\usepackage{array}\n",
    "\\usepackage{multirow}\n",
    "\\usepackage{wrapfig}\n",
    "\\usepackage{float}\n",
    "\\usepackage{colortbl}\n",
    "\\usepackage{pdflscape}\n",
    "\\usepackage{tabu}\n",
    "\\usepackage{threeparttable}\n",
    "\\usepackage{threeparttablex}\n",
    "\\usepackage[normalem]{ulem}\n",
    "\\usepackage{makecell}\n",
    "\\usepackage{xcolor}\n",
    "\\usepackage[margin=1in]{geometry}\n",
    "\\renewcommand{\\thetable}{S\\arabic{table}}\n",
    "\\usepackage{caption}\n",
    "\\captionsetup[table]{skip=10pt, font=bf}\n",
    "\\begin{document}\n",
    "\\setcounter{table}{2}\n",
    "\\thispagestyle{empty}\n",
    "\\begin{landscape}\n",
    "\\begin{table}[H]\n",
    "\\centering\\renewcommand\\cellalign{lc}\n",
    "\\setcellgapes{3pt}\\makegapedcells\n",
    "\\centering\n",
    "\\caption{Comparing Parenting with Hope and Hope Groups across global regions and crisis settings: bereaved next-of-kin caregivers in Colombia (2024-2025) versus Ukrainian caregivers amidst war and displacement (2023)}\n",
    "\\begin{threeparttable}\n",
    "\\resizebox*{!}{0.55\\textwidth}\n",
    "{\n",
    "\\small\n",
    "\\centering\n",
    paste0(latex_table1[1:3], collapse = "\n"),
    "& & & \\multicolumn{4}{c|}{\\textbf{Colombia}} & \\multicolumn{4}{c}{\\textbf{Ukraine}} \\\\ \n",
    paste0(latex_table1[4:5], collapse = "\n"),
    "\\textbf{Primary} & & & & & & & & & & \\\\ \n",
    paste0(latex_table1[6:12], collapse = "\n"),
    "\\midrule\\textbf{Secondary} & & & & & & & & & & \\\\ \n",
    paste0(latex_table2[6:9], collapse = "\n"),
    "\\multicolumn{7}{l}{$^\\dagger$ Unit of outcome: frequency of the two categories 'most of the time' and 'all of the time'.} \\\\ \n",    
    "\\multicolumn{7}{l}{$^\\ddagger$ Unit of outcome: mean days per week.} \\\\ \n",
    paste0(latex_table2[10], collapse = "\n"),
    "}\n", 
    "\\end{threeparttable}\n",
    "\\end{table}\n",
    "\\end{landscape}\n",
    "\\end{document}"
)

# Write LaTeX file
latex_file <- paste0(output_file_prefix, "_supp_table_3.tex")
writeLines(latex_doc, latex_file)

# Compile to PDF
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))
system(paste0("cd ", dirname(latex_file), " && pdflatex -interaction=nonstopmode ", basename(latex_file)))  # Run twice for proper formatting

cat("\nSupplementary Table 2 saved to:\n")
cat("  CSV: ", paste0(output_file_prefix, "_supp_table_3.csv"), "\n")
cat("  LaTeX: ", latex_file, "\n")
cat("  PDF: ", paste0(output_file_prefix, "_supp_table_3.pdf"), "\n")

```

## Figure 2

```{r plot-main-figure-2, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_primary_endpoints_grouped.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"


# Recode group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope and Resilience"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression and Anxiety']

# Plot A: Categorical mental health
tmp_cat <- subset(pos, item_type == "categorical" & 
    group_label_long == "Caregiver Depression and Anxiety" & 
    variable %in% c( "Baseline", "Endline")
    )
tmp_cat[, time_label := factor(variable, levels = c("Baseline", "Endline"))]

# Get ratio data for labels
tmp_ratio_cat <- subset(pos, item_type == "categorical" & 
    group_label_long == "Caregiver Depression and Anxiety" & 
    variable == "ratio2"
    )
tmp_ratio_cat[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
tmp_mean_cat <- tmp_cat[, list(y_pos = mean(median)), by = c("group_label_long")]
tmp_ratio_cat <- merge(tmp_ratio_cat, tmp_mean_cat, by = c("group_label_long"))
tmp_ratio_cat[, y_pos_adjusted := y_pos]

# Create plot A without faceting (or with fixed width)
plot_a <- ggplot(tmp_cat, aes(x = time_label, y = median)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(group = 1), linewidth = 1, color = "#CE78B3FF") +
    geom_point(size = 2.5, color = "#CE78B3FF") +
    geom_label(
        data = tmp_ratio_cat,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = seq(0, 1, 0.2), limits = c(0, 1), labels = scales::percent, expand = c(0,0)) +
    labs(
        x = "",
        y = "Frequency per week of categories\n'most of the time' + 'all of the time'"
    ) +
    facet_wrap(~ group_label_long, ncol = 2) +
    coord_cartesian(clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10, face = "bold"),
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    )

# Plot B: Out-of-7 items
tmp <- subset(pos, item_type == "out-of-7" & 
    variable %in% c("Baseline", "Endline")
    )
tmp[, time_label := factor(variable, levels = c("Baseline", "Endline"))]

# Recode item_high_label for display
tmp[, item_high_label := ifelse(item_high_label == "lower_is_better", "Negative outcomes improving", "Positive outcomes improving")]
tmp[, item_high_label := factor(item_high_label, levels = c("Positive outcomes improving", "Negative outcomes improving"))]

# Get ratio data for labels
tmp_ratio <- subset(pos, item_type == "out-of-7" & 
    variable == "ratio2"
    )
tmp_ratio[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
# Recode item_high_label for display in ratio data too
tmp_ratio[, item_high_label := ifelse(item_high_label == "lower_is_better", "Negative outcomes improving", "Positive outcomes improving")]
tmp_ratio[, item_high_label := factor(item_high_label, levels = c("Positive outcomes improving", "Negative outcomes improving"))]
tmp_mean <- tmp[, list(y_pos = mean(median)), by = c("group_label_long", "item_high_label")]
tmp_ratio <- merge(tmp_ratio, tmp_mean, by = c("group_label_long", "item_high_label"))
tmp_ratio[, y_pos_adjusted := y_pos]

# Create plot B
plot_b <- ggplot(tmp, aes(x = time_label, y = median, color = item_high_label)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(group = 1), linewidth = 1) +
    geom_point(size = 2.5) +
    geom_label(
        data = tmp_ratio,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        color = "black",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    facet_wrap(~ group_label_long, ncol = 3, scales = "free_y") +
    scale_color_manual(
        values = c("Positive outcomes improving" = "#573B88FF", "Negative outcomes improving" = "#CE78B3FF"),
        name = "Direction"
    ) +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = 0:7, expand = c(0,0)) +
    labs(
        x = "",
        y = "Mean days per week\n\n"
    ) +
    coord_cartesian(ylim = c(0, 7), clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10, face = "bold"),
        plot.title = element_text(face = "bold", size = 12),
        legend.position = "bottom",
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    ) +
    guides(color = guide_legend(nrow = 1))

# Create top row with plot_a on left and empty space on right
top_row <- plot_grid(plot_a, NULL, ncol = 3, 
    rel_widths = c(1.2, 1, 1), labels = c("a", ""))
# Stack top row with plot_b that spans full width, with axis alignment
combined_plot <- plot_grid(top_row, plot_b, 
    ncol = 1, nrow = 2, rel_heights = c(1.2, 3), 
    labels = c("", "b"))

# Save combined plot
ggsave(
    filename = paste0(output_file_prefix, "_figure_2.pdf"),
    plot = combined_plot,
    width = 14,
    height = 17,
    dpi = 300
)
```

## Figure 3
```{r plot-main-figure-2, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=10}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_primary_endpoints_grouped.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
pos[, analysis := 'prepost']

dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-matched-ps-tsd")
tmp <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_matched_ps_tsd_primary_endpoints_grouped.rds"))
tmp <- subset(tmp, variable %in% c('Baseline','Endline','ratio2','diff2'))
tmp[, analysis := 'quasiexp']
pos <- rbind(pos, tmp, fill = TRUE)
set(pos, NULL, "variable", pos[, gsub("Baseline", "bl", variable)])
set(pos, NULL, "variable", pos[, gsub("Endline", "el", variable)])
pos <- subset(pos, variable == 'ratio2')

output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"

# Recode group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope and Resilience"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression and Anxiety']

pos[, item_high_label := ifelse(item_high_label == "lower_is_better", "Negative outcomes improving", "Positive outcomes improving")]
pos[, item_high_label := factor(item_high_label, levels = c("Positive outcomes improving", "Negative outcomes improving"))]

pos[, analysis_label := ifelse(analysis == "prepost", "Pre-Post analysis", "Quasi-experimental analysis")]
pos[, analysis_label := factor(analysis_label, levels = c("Quasi-experimental analysis", "Pre-Post analysis"))]

p <- ggplot(pos, aes(x = analysis_label)) +
    geom_col(
        aes(y = median, fill = item_high_label), 
        colour = 'transparent'
        ) +
    geom_boxplot(aes(ymin = q_lower, lower = iqr_lower, middle = median, upper = iqr_upper, ymax = q_upper), 
        colour = "black",
        fill = 'transparent',
        width = 0.35,
        stat = "identity",
        outlier.shape = NA) +
    scale_y_continuous(
        labels = scales::percent, 
        breaks = seq(-1.5, 1.5, by = 0.5),
        limits = c(-1.9, 1.9),
        expand = c(0,0)
    ) +
    facet_wrap(group_label_long ~ ., ncol = 3) +
    labs(
        x = "Analysis type", 
        y = "Percent change (Endline vs Baseline)"
        ) +
    scale_fill_manual(
        values = c("Positive outcomes improving" = "#573B88FF", "Negative outcomes improving" = "#CE78B3FF"),
        name = "Direction"
        ) +
    coord_flip() +
    theme_bw() +
    theme(
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom"
        )
ggsave(
    filename = paste0(output_file_prefix, "_figure_3.pdf"),
    plot = p,
    width = 14,
    height = 7,
    dpi = 300
)
```


## Supplementary Figure 3

```{r plot-figure-2, include=TRUE, eval=TRUE, echo=TRUE, message=FALSE, tidy=FALSE, fig.width=12, fig.height=16}
dir_out_pcm <- file.path(dir_out_base, "colombia-plots-tables-for-paper-pcm-260413-ps-tsd")
pos <- readRDS(file.path(dir_out_pcm, "pcm_1_fit_ps_tsd_primary_endpoints_detailed.rds"))
pos <- subset(pos, variable %in% c('Baseline','Endline','ratio2','diff2'))
output_file_prefix <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/paper_Hope_Groups_effectiveness_Colombia/v260417"

# Rename group labels for display
pos[group_label_long == "Caregiver resilience", group_label_long := "Caregiver Hope and Resilience"]
pos[group_label_long == "Caregiver monitoring child", group_label_long := "Caregiver monitoring"]
pos[group_label_long == "Caregiver exercising physical or emotional violence", group_label_long := "Violence against children"]
pos[group_label_long == "Caregiver mental health", group_label_long := 'Caregiver Depression and Anxiety']

# Plot A: Categorical mental health items
tmp_cat <- subset(pos, item_type == "categorical" & 
    group_label_long == "Caregiver Depression and Anxiety" & 
    variable %in% c("Baseline", "Endline")
    )
tmp_cat[, time_label := factor(variable, levels = c("Baseline", "Endline"))]

# Create facet label combining group and item
tmp_cat[, facet_label := paste0(group_label_long, "\n(", item_label_short, ")")]

# Get ratio data for labels and merge with median values for positioning
tmp_ratio_cat <- subset(pos, item_type == "categorical" & 
    group_label_long == "Caregiver Depression and Anxiety" & 
    variable == "ratio2"
    )
tmp_ratio_cat[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
tmp_ratio_cat[, facet_label := paste0(group_label_long, "\n(", item_label_short, ")")]
# Get the mean of baseline and endline for each item to position the label
tmp_mean_cat <- tmp_cat[, list(y_pos = mean(median)), by = c("facet_label")]
tmp_ratio_cat <- merge(tmp_ratio_cat, tmp_mean_cat, by = c("facet_label"))
# Add vertical offset to prevent label overlap within each facet
tmp_ratio_cat <- tmp_ratio_cat[order(facet_label, y_pos)]
tmp_ratio_cat[, label_offset := 0]
tmp_ratio_cat[, y_pos_adjusted := y_pos + label_offset]

# Create plot A for categorical mental health
plot_a <- ggplot(tmp_cat, aes(x = time_label, y = median)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(group = 1), linewidth = 1, color = "#CE78B3FF") +
    geom_point(size = 2.5, color = "#CE78B3FF") +
    geom_label(
        data = tmp_ratio_cat,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = seq(0, 1, 0.2), limits = c(0, 1), labels = scales::percent) +
    labs(
        x = "",
        y = "Frequency per week of categories\n'most of the time' + 'all of the time'"
    ) +
    facet_wrap(~ facet_label, ncol = 3) +
    coord_cartesian(clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(face = "bold", size = 12),
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    )

# Plot B: Out-of-7 items
tmp <- subset(pos, item_type == "out-of-7" & 
    variable %in% c("Baseline", "Endline")
    )
tmp[, time_label := factor(variable, levels = c("Baseline", "Endline"))]

# Recode item_high_label for display
tmp[, item_high_label := ifelse(item_high_label == "lower_is_better", "Negative outcomes improving", "Positive outcomes improving")]
tmp[, item_high_label := factor(item_high_label, levels = c("Positive outcomes improving", "Negative outcomes improving"))]

# Get ratio data for labels and merge with median values for positioning
tmp_ratio <- subset(pos, item_type == "out-of-7" & 
    variable == "ratio2"
    )
tmp_ratio[, ratio_pct := paste0(ifelse(median > 0, "+", ""), round(median * 100, 0), "%")]
# Get the mean of baseline and endline for each item to position the label
tmp_mean <- tmp[, list(y_pos = mean(median)), by = c("item_label_short", "item_high_label", "group_label_long")]
tmp_ratio <- merge(tmp_ratio, tmp_mean, by = c("item_label_short", "item_high_label", "group_label_long"))
# Add vertical offset to prevent label overlap within facets
tmp_ratio <- tmp_ratio[order(group_label_long, y_pos)]
tmp_ratio[, label_offset := seq_len(.N) * 1.0 - mean(seq_len(.N) * 1.0), by = "group_label_long"]
tmp_ratio[, y_pos_adjusted := y_pos + label_offset]

# Create plot B
plot_b <- ggplot(tmp, aes(x = time_label, y = median, group = item_label_short, 
                     color = item_high_label)) +
    geom_errorbar(
        aes(ymin = q_lower, ymax = q_upper),
        width = 0.05,
        color = "black",
        alpha = 0.5
    ) +
    geom_line(aes(linetype = item_label_short), linewidth = 1) +
    geom_point(size = 2.5) +
    geom_text(
        data = subset(tmp, variable == "Endline"),
        aes(label = item_label_short),
        hjust = -0.3,
        size = 3,
        color = "black",
        show.legend = FALSE
    ) +
    geom_label(
        data = tmp_ratio,
        aes(x = 1.5, y = y_pos_adjusted, label = ratio_pct),
        size = 3.75,
        fontface = "bold",
        color = "black",
        label.padding = unit(0.2, "lines"),
        label.size = 0.5,
        show.legend = FALSE
    ) +
    facet_wrap(~ group_label_long, ncol = 3, scales = "free_y") +
    scale_color_manual(
        values = c("Positive outcomes improving" = "#573B88FF", "Negative outcomes improving" = "#CE78B3FF"),
        name = "Direction"
    ) +
    scale_linetype_discrete(guide = "none") +
    scale_x_discrete(expand = expansion(mult = c(0.1, 0.3))) +
    scale_y_continuous(breaks = 0:7) +
    labs(
        x = "",
        y = "Mean days per week\n"
    ) +
    coord_cartesian(ylim = c(0, 7), clip = "off") +
    theme_bw() +
    theme(
        axis.text.x = element_text(angle = 45, hjust = 1),
        strip.text = element_text(size = 10),
        plot.title = element_text(face = "bold", size = 12),
        legend.position = "bottom",
        plot.margin = margin(5.5, 40, 5.5, 5.5, "pt")
    ) +
    guides(color = guide_legend(nrow = 1))

# Combine plots
combined_plot <- ggpubr::ggarrange(plot_a, plot_b, ncol = 1, nrow = 2, heights = c(2, 3), labels = c("a", "b"), align = "v")

# Save combined plot
ggsave(
    filename = paste0(output_file_prefix, "_supp_figure_3.pdf"),
    plot = combined_plot,
    width = 14,
    height = 17,
    dpi = 300
)
```

# Session info
```{r session-info, include=TRUE, eval=TRUE, message=FALSE, echo=FALSE, warning=FALSE, tidy=TRUE}
sessionInfo()
```
