---
title: "Compare Likert outcome models on HPC"
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2:
    toc: TRUE
    toc_float: TRUE
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
---

<style type="text/css">
h1{
  font-size: 24pt;
}
h2{
  font-size: 18pt;
}
body{
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

This vignette demonstrates how to submit item response model comparison jobs to an HPC cluster using PBS scheduling. The workflow involves:

1. Creating a JSON configuration file with parameters for all model runs
2. Generating a PBS job submission script
3. Submitting the job to the HPC scheduler as a job array

We compare four different IRT models fitted to the Colombia data:
- Ordered Logistic Model (v251222)
- Credit Model (v251223)
- Credit Model (v251224)
- Partial Credit Model (v251224)

Each model is fitted with 10 different random seeds, for a total of 40 runs.

# Load packages and functions

```{r load-packages, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE}
library(jsonlite)
library(here)

source(here::here("R", "hpc_submit_generic_job.R"))
```

# Define directories and job parameters

```{r define-paths, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE}
# Define directories
if (grepl("^/rds/general/user/or105", here::here())) {
    # Working on HPC
    on_hpc <- TRUE
    dir_data <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups/data"
    dir_out_base <- "/rds/general/user/or105/home/WORK/2025_project_Hope_Groups"
} else {
    # Working locally
    on_hpc <- FALSE
    dir_data <- "/Users/or105/Library/CloudStorage/OneDrive-ImperialCollegeLondon/OR_Work/2025/2025_project_Hope_Groups/data"
    dir_out_base <- "/Users/or105/sandbox"
}

# Define output directories for each model
dir_out_ol <- file.path(dir_out_base, "colombia-run-orderedlogistic-251222b")
dir_out_cm_v251223 <- file.path(dir_out_base, "colombia-run-creditmodel-251223")
dir_out_cm_v251224 <- file.path(dir_out_base, "colombia-run-creditmodel-251224")
dir_out_pcm <- file.path(dir_out_base, "colombia-run-partialcreditmodel-251224")

# Create output directories if they don't exist
for (dir_out in c(dir_out_ol, dir_out_cm_v251223, dir_out_cm_v251224, dir_out_pcm)) {
    if (!dir.exists(dir_out)) {
        dir.create(dir_out, recursive = TRUE)
    }
    dir_logs <- file.path(dir_out, "logs")
    if (!dir.exists(dir_logs)) {
        dir.create(dir_logs, recursive = TRUE)
    }
}

# Create comparison output directory
dir_comparison <- file.path(dir_out_base, "colombia-model-comparison")
if (!dir.exists(dir_comparison)) {
    dir.create(dir_comparison, recursive = TRUE)
}

# Define job name
job_name <- paste0("compare_models_", format(Sys.time(), "%Y-%m-%d-%H-%M-%S"))
```

# Load and preprocess data

```{r load-and-preprocess-data, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE}
library(data.table)

# Define data file
file_data <- file.path(dir_data, "Colombia_data_baseline_endline_itemised_250927.csv")

# Source the data reading function
source(here::here("R", "read_data_colombia.R"))

# Load and preprocess data
cat("Loading and preprocessing data...\n")
tmp <- read_data_colombia(file_data)
dp <- copy(tmp$dp)
dit <- copy(tmp$dit)
dmeta <- copy(tmp$dmeta)

dp1 <- subset(dp, !grepl("agg", item_label))
dp1[, time := time + 1L]
dp1[, y_stan := y + 1L]
tmp <- CJ(
    item_label = sort(unique(dp1$item_label)),
    time = unique(dp1$time)
)
tmp[, item_type := ifelse(
    grepl("CG-MH", item_label), "categorical", "out-of-7"
)]
tmp <- tmp[
    , list(
        item_label = item_label, time = time,
        item_time_id = seq_along(item_label)
    ),
    by = "item_type"
]
dp1 <- merge(dp1, tmp, by = c("item_label", "time"))
setkey(dp1, pid, time, item_label)
dp1[, oid := .I]
setkey(dp1, oid)
tmp <- dp1[, list(oid = oid, oidt = seq_along(y_stan)), by = "item_type"]
dp1 <- merge(dp1, tmp, by = c("item_type", "oid"))
setkey(dp1, pid, time, item_label)

cat("Total observations read:", nrow(dp1), "\n")
cat("Number of items:", nrow(dit), "\n\n")

# Save preprocessed data
data_file <- file.path(dir_comparison, "data_inputs.rda")
save(dp1, dit, file = data_file)
cat("Saved preprocessed data to:", data_file, "\n")
```

# Create JSON configuration file

```{r create-json-config, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE}
# Define seeds for multiple runs
seeds <- c(123L, 456L, 789L, 1011L, 1213L, 1415L, 1617L, 1819L, 2021L, 2223L)

# Define model configurations
models <- list(
    list(
        model_name = "ordered_logit",
        model_version = "v251222",
        stan_file = here::here("src", "stan", "ordered_logit_2cats_v251222.stan"),
        dir_out = dir_out_ol,
        output_prefix = "ordlog_1"
    ),
    list(
        model_name = "credit_model",
        model_version = "v251223",
        stan_file = here::here("src", "stan", "credit_model_2cats_v251223.stan"),
        dir_out = dir_out_cm_v251223,
        output_prefix = "cm_2"
    ),
    list(
        model_name = "credit_model",
        model_version = "v251224",
        stan_file = here::here("src", "stan", "credit_model_2cats_v251224.stan"),
        dir_out = dir_out_cm_v251224,
        output_prefix = "cm_3"
    ),
    list(
        model_name = "partial_credit_model",
        model_version = "v251224",
        stan_file = here::here("src", "stan", "partial_credit_model_2cats_v251224.stan"),
        dir_out = dir_out_pcm,
        output_prefix = "pcm_1"
    )
)

# Create all run configurations (4 models × 10 seeds = 40 runs)
runs <- list()
run_idx <- 1
for (model in models) {
    for (seed in seeds) {
        runs[[run_idx]] <- list(
            model_name = model$model_name,
            model_version = model$model_version,
            stan_file = model$stan_file,
            seed = seed,
            output_prefix = model$output_prefix,
            dir_out = model$dir_out
        )
        run_idx <- run_idx + 1
    }
}

# Create configuration with all runs
config <- list(
    runs = runs,
    data_file = data_file,
    dir_out = dir_comparison,  # Main output directory for the job
    chains = 4L,
    parallel_chains = ifelse(on_hpc, 4L, 4L),
    threads_per_chain = 1L,
    iter_warmup = 500L,
    iter_sampling = 500L,
    with_core_analyses = TRUE,
    with_additional_analyses = TRUE,
    show_messages = TRUE,
    show_exceptions = TRUE
)

# Save configuration to JSON file
json_file <- file.path(dir_comparison, paste0(job_name, "_config.json"))
write_json(config, json_file, pretty = TRUE, auto_unbox = TRUE)

cat("Created JSON configuration file:", json_file, "\n")
cat("Total number of runs:", length(runs), "\n")
cat("Number of models:", length(models), "\n")
cat("Number of seeds per model:", length(seeds), "\n")
```

# Create and submit PBS job

```{r create-pbs-script, include=TRUE, eval=FALSE, message=FALSE, echo=TRUE, warning=FALSE}
# Define PBS job parameters
pbs_config <- list(
    script_path = here::here("R", "fit_item_response_models.Rscript"),
    json_path = json_file,
    job_name = job_name,
    output_dir = file.path(dir_comparison, "logs"),
    walltime = "12:00:00",
    memory = "16gb",
    ncpus = 4,
    narray = length(runs),
    email = NULL, # Set to your email address for notifications
    email_options = "abe", # a=abort, b=begin, e=end
    header = gsub('(^|\\n)[ \\t]+', '\\1', '
      module load miniforge/3 tools/prod zlib libxml2/2.11.5-GCCcore-13.2.0
      eval "$(~/miniforge3/bin/conda shell.bash hook)"
      eval "$(mamba shell hook --shell bash)"
      mamba activate birtistic
    '),
    submit = TRUE # Set to TRUE to submit immediately
)

# Create PBS submission script
pbs_script <- do.call(hpc_submit_generic_job, pbs_config)

cat("\nPBS submission script created:", pbs_script, "\n")
```

# Results

After all jobs complete, you can aggregate results across models and seeds:

```{r aggregate-results, include=TRUE, eval=FALSE, message=FALSE, echo=TRUE, warning=FALSE}
library(data.table)
library(loo)

# Define seeds for multiple runs
seeds <- c(123L, 456L, 789L, 1011L, 1213L, 1415L, 1617L, 1819L, 2021L, 2223L)

# Process models for each seed sequentially
for (seed in seeds) {
    cat("\n=== Processing seed", seed, "===\n")
    
    # Define file paths for this seed
    ol_rds <- file.path(dir_out_ol, paste0("seed-", seed), "ordlog_1_fit_alldata_stan.rds")
    cm_v251223_rds <- file.path(dir_out_cm_v251223, paste0("seed-", seed), "cm_2_fit_alldata_stan.rds")
    cm_v251224_rds <- file.path(dir_out_cm_v251224, paste0("seed-", seed), "cm_3_fit_alldata_stan.rds")
    pcm_v251224_rds <- file.path(dir_out_pcm, paste0("seed-", seed), "pcm_1_fit_alldata_stan.rds")
    
    # Check if all files exist
    all_files_exist <- all(file.exists(c(ol_rds, cm_v251223_rds, cm_v251224_rds, pcm_v251224_rds)))
    if (!all_files_exist) {
        cat("  Warning: Not all model files exist for seed", seed, ". Skipping.\n")
        next
    }
    
    # Process ordered logit model
    cat("  --- Evaluating ordered logit model ---\n")
    ol_fit <- readRDS(ol_rds)
    log_lik_ol <- ol_fit$draws("log_lik", format = "matrix")
    loo_ol <- loo::loo(log_lik_ol)
    waic_ol <- loo::waic(log_lik_ol)
    ol_fit <- NULL
    log_lik_ol <- NULL
    gc()
    
    # Process credit model v251223
    cat("  --- Evaluating credit model v251223 ---\n")
    cm_fit_v251223 <- readRDS(cm_v251223_rds)
    log_lik_cm_v251223 <- cm_fit_v251223$draws("log_lik", format = "matrix")
    loo_cm_v251223 <- loo::loo(log_lik_cm_v251223)
    waic_cm_v251223 <- loo::waic(log_lik_cm_v251223)
    cm_fit_v251223 <- NULL
    log_lik_cm_v251223 <- NULL
    gc()
    
    # Process credit model v251224
    cat("  --- Evaluating credit model v251224 ---\n")
    cm_fit_v251224 <- readRDS(cm_v251224_rds)
    log_lik_cm_v251224 <- cm_fit_v251224$draws("log_lik", format = "matrix")
    loo_cm_v251224 <- loo::loo(log_lik_cm_v251224)
    waic_cm_v251224 <- loo::waic(log_lik_cm_v251224)
    cm_fit_v251224 <- NULL
    log_lik_cm_v251224 <- NULL
    gc()
    
    # Process partial credit model v251224
    cat("  --- Evaluating partial credit model v251224 ---\n")
    pcm_fit_v251224 <- readRDS(pcm_v251224_rds)
    log_lik_pcm_v251224 <- pcm_fit_v251224$draws("log_lik", format = "matrix")
    loo_pcm_v251224 <- loo::loo(log_lik_pcm_v251224)
    waic_pcm_v251224 <- loo::waic(log_lik_pcm_v251224)
    pcm_fit_v251224 <- NULL
    log_lik_pcm_v251224 <- NULL
    gc()
    
    # Load convergence diagnostics
    cat("  --- Loading convergence diagnostics ---\n")
    conv_ol <- fread(file.path(dir_out_ol, paste0("seed-", seed), "ordlog_1_fit_alldata_convergence_mixing.csv"))
    conv_cm_v251223 <- fread(file.path(dir_out_cm_v251223, paste0("seed-", seed), "cm_2_fit_alldata_convergence_mixing.csv"))
    conv_cm_v251224 <- fread(file.path(dir_out_cm_v251224, paste0("seed-", seed), "cm_3_fit_alldata_convergence_mixing.csv"))
    conv_pcm_v251224 <- fread(file.path(dir_out_pcm, paste0("seed-", seed), "pcm_1_fit_alldata_convergence_mixing.csv"))
    
    # Load timing data
    cat("  --- Loading timing data ---\n")
    timing_ol <- fread(file.path(dir_out_ol, paste0("seed-", seed), "ordlog_1_fit_alldata_timing.csv"))
    timing_cm_v251223 <- fread(file.path(dir_out_cm_v251223, paste0("seed-", seed), "cm_2_fit_alldata_timing.csv"))
    timing_cm_v251224 <- fread(file.path(dir_out_cm_v251224, paste0("seed-", seed), "cm_3_fit_alldata_timing.csv"))
    timing_pcm_v251224 <- fread(file.path(dir_out_pcm, paste0("seed-", seed), "pcm_1_fit_alldata_timing.csv"))
    
    # Load Brier scores
    cat("  --- Loading Brier scores ---\n")
    brier_ol <- fread(file.path(dir_out_ol, paste0("seed-", seed), "ordlog_1_fit_alldata_ordered_brierscore.csv"))
    brier_cm_v251223 <- fread(file.path(dir_out_cm_v251223, paste0("seed-", seed), "cm_2_fit_alldata_ordered_brierscore.csv"))
    brier_cm_v251224 <- fread(file.path(dir_out_cm_v251224, paste0("seed-", seed), "cm_3_fit_alldata_ordered_brierscore.csv"))
    brier_pcm_v251224 <- fread(file.path(dir_out_pcm, paste0("seed-", seed), "pcm_1_fit_alldata_ordered_brierscore.csv"))
    
    # Add model identifier to each Brier score dataset
    brier_ol[, Model := "Ordered Logistic (v251222)"]
    brier_cm_v251223[, Model := "Credit Model (v251223)"]
    brier_cm_v251224[, Model := "Credit Model (v251224)"]
    brier_pcm_v251224[, Model := "Partial Credit Model (v251224)"]
    
    # Combine all Brier scores for this seed
    brier_seed <- rbindlist(list(brier_ol, brier_cm_v251223, brier_cm_v251224, brier_pcm_v251224))
    brier_seed[, seed := seed]
    
    # Save question-level Brier scores
    fwrite(brier_seed,
           file = file.path(dir_comparison, paste0("colombia_brier_scores_by_question_seed", seed, ".csv")))
    
    # Compute mean Brier score across questions for comparison table
    brier_summary <- brier_seed[, 
        list(median_brier_score = median(median_brier_score),
             max_brier_score = max(median_brier_score)
        ), 
        by = c('Model', 'item_type', 'seed')
    ]
    
    # Create comparison table for this seed
    comparison_seed <- data.table(
        seed = seed,
        Model = c("Ordered Logistic (v251222)", 
                  "Credit Model (v251223)", "Credit Model (v251224)", 
                  "Partial Credit Model (v251224)"),
        ELPD_loo = c(loo_ol$estimates["elpd_loo", "Estimate"],
                     loo_cm_v251223$estimates["elpd_loo", "Estimate"],
                     loo_cm_v251224$estimates["elpd_loo", "Estimate"],
                     loo_pcm_v251224$estimates["elpd_loo", "Estimate"]),
        ELPD_loo_SE = c(loo_ol$estimates["elpd_loo", "SE"],
                        loo_cm_v251223$estimates["elpd_loo", "SE"],
                        loo_cm_v251224$estimates["elpd_loo", "SE"],
                        loo_pcm_v251224$estimates["elpd_loo", "SE"]),
        WAIC = c(waic_ol$estimates["elpd_waic", "Estimate"],
                 waic_cm_v251223$estimates["elpd_waic", "Estimate"],
                 waic_cm_v251224$estimates["elpd_waic", "Estimate"],
                 waic_pcm_v251224$estimates["elpd_waic", "Estimate"]),
        WAIC_SE = c(waic_ol$estimates["elpd_waic", "SE"],
                    waic_cm_v251223$estimates["elpd_waic", "SE"],
                    waic_cm_v251224$estimates["elpd_waic", "SE"],
                    waic_pcm_v251224$estimates["elpd_waic", "SE"]),
        min_ess_bulk = c(min(conv_ol$ess_bulk, na.rm = TRUE),
                         min(conv_cm_v251223$ess_bulk, na.rm = TRUE),
                         min(conv_cm_v251224$ess_bulk, na.rm = TRUE),
                         min(conv_pcm_v251224$ess_bulk, na.rm = TRUE)),
        min_ess_tail = c(min(conv_ol$ess_tail, na.rm = TRUE),
                         min(conv_cm_v251223$ess_tail, na.rm = TRUE),
                         min(conv_cm_v251224$ess_tail, na.rm = TRUE),
                         min(conv_pcm_v251224$ess_tail, na.rm = TRUE)),
        max_rhat = c(max(conv_ol$rhat, na.rm = TRUE),
                     max(conv_cm_v251223$rhat, na.rm = TRUE),
                     max(conv_cm_v251224$rhat, na.rm = TRUE),
                     max(conv_pcm_v251224$rhat, na.rm = TRUE)),
        max_total_chain_minutes = c(max(timing_ol$total_chain_minutes, na.rm = TRUE),
                                    max(timing_cm_v251223$total_chain_minutes, na.rm = TRUE),
                                    max(timing_cm_v251224$total_chain_minutes, na.rm = TRUE),
                                    max(timing_pcm_v251224$total_chain_minutes, na.rm = TRUE))
    )
    
    # Merge Brier scores into comparison table
    comparison_seed <- merge(comparison_seed, brier_summary, by = "Model")
    
    # Save comparison for this seed
    fwrite(comparison_seed,
           file = file.path(dir_comparison, paste0("colombia_model_comparison_2cat_seed", seed, ".csv")))
    
    # Clear variables and run gc
    loo_ol <- waic_ol <- conv_ol <- timing_ol <- brier_ol <- NULL
    loo_cm_v251223 <- waic_cm_v251223 <- conv_cm_v251223 <- timing_cm_v251223 <- brier_cm_v251223 <- NULL
    loo_cm_v251224 <- waic_cm_v251224 <- conv_cm_v251224 <- timing_cm_v251224 <- brier_cm_v251224 <- NULL
    loo_pcm_v251224 <- waic_pcm_v251224 <- conv_pcm_v251224 <- timing_pcm_v251224 <- brier_pcm_v251224 <- NULL
    brier_seed <- brier_summary <- comparison_seed <- NULL
    gc()
}

# Aggregate results across seeds
cat("\n=== Aggregating results across seeds ===\n")
dc <- rbindlist(lapply(seeds, function(seed) {
    csv_file <- file.path(dir_comparison, paste0("colombia_model_comparison_2cat_seed", seed, ".csv"))
    if (file.exists(csv_file)) {
        fread(csv_file)
    } else {
        NULL
    }
}))

if (nrow(dc) > 0) {
    dc[, seed.y := NULL]
    if ("seed.x" %in% names(dc)) {
        setnames(dc, "seed.x", "seed")
    }
    dc <- melt(dc, id.vars = c("Model", "seed", "item_type"))
    dc <- dc[, list(value = c(mean(value), min(value), max(value)), 
                    value_label = c('mean', 'min', 'max')), 
             by = c("Model", "variable")]
    dc <- dcast(dc, Model + value_label ~ variable, value.var = "value")
    
    # Round for display
    dc[, ELPD_loo := round(ELPD_loo, 1)]
    dc[, ELPD_loo_SE := round(ELPD_loo_SE, 1)]
    dc[, WAIC := round(WAIC, 1)]
    dc[, WAIC_SE := round(WAIC_SE, 1)]
    dc[, min_ess_bulk := round(min_ess_bulk, 0)]
    dc[, min_ess_tail := round(min_ess_tail, 0)]
    dc[, max_rhat := round(max_rhat, 3)]
    dc[, max_total_chain_minutes := round(max_total_chain_minutes, 2)]
    dc[, median_brier_score := round(median_brier_score, 4)]
    dc[, max_brier_score := round(max_brier_score, 4)]
    
    fwrite(dc, 
           file = file.path(dir_comparison, "colombia_model_comparison_2cat.csv"))
    
    cat("\nFinal comparison table saved to:", 
        file.path(dir_comparison, "colombia_model_comparison_2cat.csv"), "\n")
} else {
    cat("No results found to aggregate.\n")
}
```

# Session information

```{r session-info, include=TRUE, eval=TRUE, message=FALSE, echo=TRUE, warning=FALSE}
sessionInfo()
```
